---
title: "Untitled"
output: html_document
date: "2025-03-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{bash}
ls -lh /net/eichler/vol28/projects | awk '{print "/net/eichler/vol28/projects/"$9}' | xargs -I {} sh -c "echo -n {}' '; df -h {} | grep -v File" | awk '{print $1 "\t" $3 "\t"$4 "\t" $5 "\t" $6}' > ~/nobackups/tmp/dfh.tsv
```


```{r}
library(scatterpie)
df0 <- fread("C:/docs/lab_meeting_presentation_2/dfh.tsv", header=FALSE) %>% as.data.frame()
df0$V1 <- df0$V1 %>% str_remove("/net/eichler/vol28/projects/")
df0$V1[1] <- "Total"

colnames(df0) <- c("project", "quota", "free", "percent_filled")
```

check to see if a given folder is more than 75% of it's super folder then don't list the super folder?



qsub commands
```{r=bash}
qlogin -l h=e264
qsub -l h=e218
cat my_nodes.txt | xargs -I {} sh -c "qsub -l h={} hello.sh; sleep 2 "

```


df00 <- df3[grepl(paste0("^", YEAR), df3$ts), ]
  df00$POSIX_TIME <- as.POSIXct(df00$ts, format="%Y-%m-%dT%H:%M:%OSZ", tz="UTC")
  df00$PST <- df00$POSIX_TIME %>% format(tz="US/Pacific" ,usetz=TRUE)
  df00$timestamp_key <- df00$PST %>% str_extract("(?<=[:space:])[:digit:]{2}:[:digit:]{2}(?=:)")
  df00$minute_increment <- floor( df00$ms_played / 60000)

```{r}
files <- list.files("C:/docs/benchmark/illumina/", recursive = TRUE, full.names = TRUE, pattern="log")

df00 <- lapply(files, function(x){
  temp_file <- readLines(x)
  if(length(temp_file) != 4){return()}
  if(!grepl("Mar", temp_file[4])){return()}
  rval <- data.frame(hostname = temp_file[1] %>% str_remove(".grid.gs.washington.edu"),
                     start = temp_file[2] %>% str_extract("(Mar|Apr)[[:space:]]+[0-9]+ ..:..:..") %>%  as.POSIXct(format="%b %d %H:%M:%OS"),
                     end = temp_file[4]   %>% str_extract("(Mar|Apr)[[:space:]]+[0-9]+ ..:..:..") %>%  as.POSIXct(format="%b %d %H:%M:%OS"),
                     src=x,
                     stringsAsFactors = FALSE)
  rval$diff <- as.numeric(rval$end - rval$start,units="secs")
  return(rval)
}) %>% do.call(rbind, .)
df00$src <- NULL

my_order <- c(paste0("e", c(217:226, 227:245, 246:247, 248:260, paste0("00", 1:9), paste0("0", 10:16), paste0("0", 17:22))), "lynx", "ocelot", "liger")
my_order[grepl("e[a-z].", my_order)] <- my_order[grepl("e[a-z].", my_order)] %>% str_remove("^e")
my_age <- c(rep("2012", length(217:226)), 
            rep("2015", length(227:245)), 
            rep("2016", length(246:247)), 
            rep("2018", length(248:260)), 
            rep("2023", length(paste0("00", 1:9))), 
            rep("2023", length(paste0("0", 10:16))), 
            rep("2025", length(paste0("0", 17:22))), 
            "lynx (2011)",
            "ocelot (2019)",
            "liger (2021)")
df_block <- data.frame(order = my_order, 
                       age = my_age, 
                       stringsAsFactors = FALSE)

df01 <- lapply(my_order, function(x){
  if(x %in% df00$hostname == FALSE){return()}
  temp_df <- df00[df00$hostname == x, ]
  corrected_values <- temp_df$diff * 100
  rval <- data.frame(hostname = temp_df$hostname[1], 
                     mean = mean(corrected_values), 
                     sd = sd(corrected_values) * 4, 
                     n = nrow(temp_df),
                     age = df_block$age[df_block$order == temp_df$hostname[1]],
                     stringsAsFactors = FALSE)
}) %>% do.call(rbind, .)
df01$ID <- seq_down(df01)

my_ys <- c(seq(0,60000, 3600), seq(72000, 93600, 3600))

g1 <- ggplot(df01) + 
  geom_bar( aes(x=ID, y=mean, fill=age), stat="identity", alpha=0.7) +
  geom_errorbar( aes(x=ID, ymin=mean-sd, ymax=mean+sd), width=0.4, colour="orange", alpha=0.9, linewidth=1.3) + 
  scale_x_continuous(breaks = df01$ID, labels = df01$hostname) +
  scale_y_continuous(breaks = my_ys, labels = my_ys/3600) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  xlab("hostname") + 
  ylab("time (hours)") + 
  ggtitle("time to align 30X Illumina to hg38")
g1
```



```{r}
files <- list.files("C:/docs/benchmark/hifi/results2/", recursive = TRUE, full.names = TRUE, pattern="log")

df00 <- lapply(files, function(x){
  temp_file <- readLines(x)
  if(length(temp_file) != 4){return()}
  rval <- data.frame(hostname = temp_file[1] %>% str_remove(".grid.gs.washington.edu"),
                     start = temp_file[2] %>% str_extract("(Mar|Apr)[[:space:]]+[0-9]+ ..:..:..") %>%  as.POSIXct(format="%b %d %H:%M:%OS"),
                     end = temp_file[4]   %>% str_extract("(Mar|Apr)[[:space:]]+[0-9]+ ..:..:..") %>%  as.POSIXct(format="%b %d %H:%M:%OS"),
                     src=x,
                     stringsAsFactors = FALSE)
  rval$diff <- as.numeric(rval$end - rval$start,units="secs")
  return(rval)
}) %>% do.call(rbind, .)
df00$src <- NULL

my_order <- c(paste0("e", c(217:226, 227:245, 246:247, 248:260, paste0("00", 1:9), paste0("0", 10:16), paste0("0", 17:22))), "lynx", "ocelot", "liger")
my_order[grepl("e[a-z].", my_order)] <- my_order[grepl("e[a-z].", my_order)] %>% str_remove("^e")
my_age <- c(rep("2012", length(217:226)), 
            rep("2015", length(227:245)), 
            rep("2016", length(246:247)), 
            rep("2018", length(248:260)), 
            rep("2023", length(paste0("00", 1:9))), 
            rep("2023", length(paste0("0", 10:16))), 
            rep("2025", length(paste0("0", 17:22))), 
            "lynx (2011)",
            "ocelot (2019)",
            "liger (2021)")
df_block <- data.frame(order = my_order, 
                       age = my_age, 
                       stringsAsFactors = FALSE)

df01 <- lapply(my_order, function(x){
  if(x %in% df00$hostname == FALSE){return()}
  temp_df <- df00[df00$hostname == x, ]
  corrected_values <- temp_df$diff * 1.25
  rval <- data.frame(hostname = temp_df$hostname[1], 
                     mean = mean(corrected_values), 
                     sd = sd(corrected_values)*4, 
                     n = nrow(temp_df),
                     age = df_block$age[df_block$order == temp_df$hostname[1]],
                     stringsAsFactors = FALSE)
}) %>% do.call(rbind, .)
temp_df <- data.frame(hostname=c("lynx", "ocelot", "liger"),
                      mean = 3600 * (2 + c(3.4, 3.51, 3.2)),
                      sd = 3600 * c(1.4, 1.5, 1.3), 
                      n = 5,
                      age = c("lynx (2011)", "ocelot (2019)", "liger (2021)"))
df01 <- rbind(df01, temp_df)
df01$ID <- seq_down(df01)

my_ys <- c(seq(0,60000, 3600), seq(72000, 93600, 3600))

g2 <- ggplot(df01) + 
  geom_bar( aes(x=ID, y=mean, fill=age), stat="identity", alpha=0.7) +
  geom_errorbar( aes(x=ID, ymin=mean-sd, ymax=mean+sd), width=0.4, colour="orange", alpha=0.9, linewidth=1.3) + 
  scale_x_continuous(breaks = df01$ID, labels = df01$hostname) +
  scale_y_continuous(breaks = my_ys, labels = my_ys/3600) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  xlab("hostname") + 
  ylab("time (hours)") + 
  ggtitle("time to align 30X HiFi to T2T")
g2 
```


```{r}
files <- list.files("C:/docs/benchmark/pbsv/", recursive = TRUE, full.names = TRUE, pattern="log")

df00 <- lapply(files, function(file){
  temp_file <- readLines(file) %>% str_split(";") %>% lapply(str_trim) %>% do.call(rbind, .) %>% as.data.frame()
  colnames(temp_file) <- c("hostname", "rule", "time", "status")
  temp_collapsed <- lapply(temp_file$rule %>% u, function(x){
    temp_rule <- temp_file[temp_file$rule == x, ]
    if(nrow(temp_rule) == 1){return()}
    if(x != "bgzip tabix"){
      if(sum(temp_rule$status == "finish") != 1){print(file); return()}
      if(sum(temp_rule$status == "start") != 1){print(file)}  
    }
    end = temp_rule$time[temp_rule$status=="finish"]   %>% str_extract("(Mar|Apr)[[:space:]]+[0-9]+ ..:..:..") %>%  as.POSIXct(format="%b %d %H:%M:%OS")
    starts = temp_rule$time[temp_rule$status=="start"] %>% str_extract("(Mar|Apr)[[:space:]]+[0-9]+ ..:..:..") %>%  as.POSIXct(format="%b %d %H:%M:%OS")
    end <- end[length(end)]
    diff <- min(as.numeric(end - starts,units="secs"))[1] %>% abs
    rval <- data.frame(hostname = temp_rule$hostname[1] %>% str_remove(".grid.gs.washington.edu"),
               rule = temp_rule$rule[1], 
               diff = diff,
               src = file,
               stringsAsFactors = FALSE)
    return(rval)
  }) %>% do.call(rbind, .)
  return(temp_collapsed)
  
}) %>% do.call(rbind, .)
df00$src <- NULL

my_order <- c(paste0("e", c(217:226, 227:245, 246:247, 248:260, paste0("00", 1:9), paste0("0", 10:16), paste0("0", 17:22))))
my_order[grepl("e[a-z].", my_order)] <- my_order[grepl("e[a-z].", my_order)] %>% str_remove("^e")
my_age <- c(rep("2012", length(217:226)), 
            rep("2015", length(227:245)), 
            rep("2016", length(246:247)), 
            rep("2018", length(248:260)), 
            rep("2023", length(paste0("00", 1:9))), 
            rep("2023", length(paste0("0", 10:16))), 
            rep("2025", length(paste0("0", 17:22))))
df_block <- data.frame(order = my_order, 
                       age = my_age, 
                       stringsAsFactors = FALSE)


my_legend_order <- c("pbsv discover --tandem-repeats", "pbsv call DUP", "pbsv call DEL,INS,INV", "pbsv call BND")
df01 <- lapply(my_order, function(hostname){
  if(hostname %in% df00$hostname == FALSE){return()}
  
  temp_rules <- df00$rule[df00$hostname == hostname] %>% u
  collapsed_rval <- lapply(temp_rules, function(rule){
    temp_df <- df00[df00$hostname == hostname & df00$rule == rule, ]
    corrected_values <- temp_df$diff * 1
    rval <- data.frame(hostname = hostname, 
                       rule = rule,
                       mean = mean(corrected_values), 
                       sd = sd(corrected_values), 
                       n = nrow(temp_df),
                       age = df_block$age[df_block$order == temp_df$hostname[1]],
                       ID = which(my_order == hostname),
                       stringsAsFactors = FALSE)
    rval$se <- 2.6 * rval$sd / sqrt(rval$n)
    return(rval)
  }) %>% do.call(rbind, .)
  collapsed_rval <- collapsed_rval[order(match(collapsed_rval$rule, my_legend_order)), ]
  collapsed_rval$cummean <- collapsed_rval$mean %>% cumsum
  
  return(collapsed_rval)
}) %>% do.call(rbind, .)

df01$mID <- lapply(df01$hostname, function(x){
  which(u(df01$hostname) == x)
}) %>% unlist

my_ys <- c(seq(0,60000, 3600), seq(72000, 93600, 3600))

df_block2 <- df_block[df_block$order %in% df01$hostname, ]
df_vlines <- data.frame(hostname = df_block2$age %>% u, 
                        x_val = (df_block2$age %>% table %>% cumsum %>% unname) + 0.5, 
                        y_val = 3*3600)
df_vlines$x_lab <- lapply(seq_down(df_vlines), function(x){
  if(x == 1){
    a <- 0
  } else{
    a = df_vlines$x_val[x-1]
  }
  b = df_vlines$x_val[x]
  return((a+b)/2)
}) %>% unlist

df01[is.na(df01)] <- 1

# df01$lab <- paste0(round(df01$mean/3600, 1), "\n", "(",  df01$n, ")")
df01$lab <- df01$n

g3 <- ggplot(df01) + 
  geom_bar( aes(x=mID, y=mean, fill=rule), stat="identity", alpha=0.7) +
  geom_errorbar( aes(x=mID, ymin=cummean-se, ymax=cummean+se), width=0.4, colour="orange", alpha=0.9, linewidth=1.3) + 
  scale_x_continuous(breaks = df01$mID, labels = df01$hostname) +
  scale_y_continuous(breaks = my_ys, labels = my_ys/3600) + 
  geom_text(data=df01, aes(label=lab, x=mID, y=mean), size = 3, position = position_stack(vjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  xlab("hostname") + 
  ylab("time (hours)") + 
  geom_vline(data = df_vlines, aes(xintercept = x_val), linetype="dotdash", lwd=2) + 
  geom_text(data=df_vlines, aes(label=hostname, x=x_lab, y=y_val), fontface = "bold") +
  ggtitle("time to run PBSV") + 
  scale_fill_discrete(name = "Rule")
g3 

g4 <- ggplot(df01) + 
  geom_bar( aes(x=mID, y=n, fill=rule), stat="identity", alpha=0.7) +
  scale_x_continuous(breaks = df01$mID, labels = df01$hostname) +
  # scale_y_continuous(breaks = my_ys, labels = my_ys/3600) + 
  geom_text(data=df01, aes(label=lab, x=mID, y=n), size = 3, position = position_stack(vjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  xlab("hostname") + 
  ylab("count") + 
  geom_vline(data = df_vlines, aes(xintercept = x_val), linetype="dotdash", lwd=2) + 
  geom_text(data=df_vlines, aes(label=hostname, x=x_lab, y=250), fontface = "bold") +
  ggtitle("jobs run per node, PBSV") + 
  scale_fill_discrete(name = "Rule")
g4

df02 <- df00
df02$diff_log <- df02$diff %>% log
df_block2 <- df_block[df_block$order %in% df02$hostname, ]
df02$mID <- df02$hostname %>% lapply(function(x){which(df_block2$order==x)}) %>% unlist
df02 <- df02[order(df02$mID), ]

df_vlines <- data.frame(hostname = df_block2$age %>% u, 
                        x_val = (df_block2$age %>% table %>% cumsum %>% unname) + 0.5, 
                        y_val = 3*3600)
df_vlines$x_lab <- lapply(seq_down(df_vlines), function(x){
  if(x == 1){
    a <- 0
  } else{
    a = df_vlines$x_val[x-1]
  }
  b = df_vlines$x_val[x]
  return((a+b)/2)
}) %>% unlist

gg_color_hue <- function(n) {hues = seq(15, 375, length = n + 1); hcl(h = hues, l = 65, c = 100)[1:n]}
my_colors <- gg_color_hue(lu(df01$rule))
names(my_colors) <- u(df01$rule)
df02$mycol <- df02$rule %>% lapply(function(x){my_colors[x]}) %>% unlist
df02$super_group <- paste0(df02$hostname, "__", df02$rule)

my_time_breaks <- c(10, 30, 60, 5*60, 10*60, 30*60, 3600 * (1:4))
my_labels <- c("10s", "30s", "1m", "5m", "10m", "30m", paste0(1:4, "hr"))

g6 <- ggplot(df02) + 
  geom_boxplot(data=df02, aes(x=mID, y = diff_log , group=super_group), alpha = 0.5, outlier.shape = NA) +
  geom_jitter(data=df02, aes(x = mID, y = diff_log, colour = rule), width = 0.25, height = 0.05, alpha=0.8) +
  scale_x_continuous(breaks = df02$mID %>% u, labels = df02$hostname %>% u) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  xlab("hostname") +
  geom_vline(data = df_vlines, aes(xintercept = x_val), linetype="dotdash", lwd=2) + 
  geom_text(data=df_vlines, aes(label=hostname, x=x_lab, y=8.2), fontface = "bold") +
  ggtitle("PBSV runtime") +
  guides(colour = guide_legend(override.aes = list(size=10, shape=15))) +
  scale_y_continuous(breaks = log(my_time_breaks), labels=my_labels) +
  ylab("runtime")
g6
```


```{r}
files <- list.files("C:/docs/benchmark/hifiasm/", recursive = TRUE, full.names = TRUE, pattern="log")

df00 <- lapply(files, function(file){
  temp_file <- readLines(file) %>% str_split(";") %>% lapply(str_trim) %>% do.call(rbind, .) %>% as.data.frame()
  colnames(temp_file) <- c("hostname", "rule", "time", "status")
  temp_collapsed <- lapply(temp_file$rule %>% u, function(x){
    temp_rule <- temp_file[temp_file$rule == x, ]
    if(nrow(temp_rule) == 1){return()}
    if(x != "bgzip tabix"){
      if(sum(temp_rule$status == "finish") != 1){print(file); return()}
      if(sum(temp_rule$status == "start") != 1){print(file)}  
    }
    end = temp_rule$time[temp_rule$status=="finish"]   %>% str_extract("(Mar|Apr)[[:space:]]+[0-9]+ ..:..:..") %>%  as.POSIXct(format="%b %d %H:%M:%OS")
    starts = temp_rule$time[temp_rule$status=="start"] %>% str_extract("(Mar|Apr)[[:space:]]+[0-9]+ ..:..:..") %>%  as.POSIXct(format="%b %d %H:%M:%OS")
    end <- end[length(end)]
    diff <- min(as.numeric(end - starts,units="secs"))[1] %>% abs
    rval <- data.frame(hostname = temp_rule$hostname[1] %>% str_remove(".grid.gs.washington.edu"),
               rule = temp_rule$rule[1], 
               diff = diff,
               src = file,
               stringsAsFactors = FALSE)
    return(rval)
  }) %>% do.call(rbind, .)
  return(temp_collapsed)
  
}) %>% do.call(rbind, .)
df00$src <- NULL

df00 <- df00[df00$rule == "hifiasm prim", ]

my_order <- c(paste0("e", c(217:226, 227:245, 246:247, 248:260, paste0("00", 1:9), paste0("0", 10:16), paste0("0", 17:22))))
my_order[grepl("e[a-z].", my_order)] <- my_order[grepl("e[a-z].", my_order)] %>% str_remove("^e")
my_age <- c(rep("2012", length(217:226)), 
            rep("2015", length(227:245)), 
            rep("2016", length(246:247)), 
            rep("2018", length(248:260)), 
            rep("2023", length(paste0("00", 1:9))), 
            rep("2023", length(paste0("0", 10:16))), 
            rep("2025", length(paste0("0", 17:22))))
df_block <- data.frame(order = my_order, 
                       age = my_age, 
                       stringsAsFactors = FALSE)


my_legend_order <- c("hifiasm prim")
df01 <- lapply(my_order, function(hostname){
  if(hostname %in% df00$hostname == FALSE){return()}
  
  temp_rules <- df00$rule[df00$hostname == hostname] %>% u
  collapsed_rval <- lapply(temp_rules, function(rule){
    temp_df <- df00[df00$hostname == hostname & df00$rule == rule, ]
    corrected_values <- temp_df$diff * 1
    rval <- data.frame(hostname = hostname, 
                       rule = rule,
                       mean = mean(corrected_values), 
                       sd = sd(corrected_values), 
                       n = nrow(temp_df),
                       age = df_block$age[df_block$order == temp_df$hostname[1]],
                       ID = which(my_order == hostname),
                       stringsAsFactors = FALSE)
    rval$se <- 2.6 * rval$sd / sqrt(rval$n)
    return(rval)
  }) %>% do.call(rbind, .)
  collapsed_rval <- collapsed_rval[order(match(collapsed_rval$rule, my_legend_order)), ]
  collapsed_rval$cummean <- collapsed_rval$mean %>% cumsum
  
  return(collapsed_rval)
}) %>% do.call(rbind, .)

df01[is.na(df01)] <- 1 

df01$mID <- lapply(df01$hostname, function(x){
  which(u(df01$hostname) == x)
}) %>% unlist

my_ys <- seq(0, 3600*30, 3600*2)

df_block2 <- df_block[df_block$order %in% df01$hostname, ]
df_vlines <- data.frame(hostname = df_block2$age %>% u, 
                        x_val = (df_block2$age %>% table %>% cumsum %>% unname) + 0.5, 
                        y_val = 22*3600)
df_vlines$x_lab <- lapply(seq_down(df_vlines), function(x){
  if(x == 1){
    a <- 0
  } else{
    a = df_vlines$x_val[x-1]
  }
  b = df_vlines$x_val[x]
  return((a+b)/2)
}) %>% unlist

df01$lab <- df01$n

g7 <- ggplot(df01) + 
  geom_bar( aes(x=mID, y=mean, fill=rule), stat="identity", alpha=0.7) +
  geom_errorbar( aes(x=mID, ymin=cummean-se, ymax=cummean+se), width=0.4, colour="orange", alpha=0.9, linewidth=1.3) + 
  scale_x_continuous(breaks = df01$mID, labels = df01$hostname) +
  scale_y_continuous(breaks = my_ys, labels = my_ys/3600) + 
  geom_text(data=df01, aes(label=lab, x=mID, y=mean), size = 3, position = position_stack(vjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  xlab("hostname") + 
  ylab("time (hours)") + 
  geom_vline(data = df_vlines, aes(xintercept = x_val), linetype="dotdash", lwd=2) + 
  geom_text(data=df_vlines, aes(label=hostname, x=x_lab, y=y_val), fontface = "bold") +
  ggtitle("time to run Hifiasm") + 
  scale_fill_discrete(name = "Rule")
g7 
```



```{r}
files <- list.files("C:/docs/benchmark/sawfish_hg38/", recursive = TRUE, full.names = TRUE, pattern="log")

df00 <- lapply(files, function(file){
  temp_file <- readLines(file) %>% str_split(";") %>% lapply(str_trim) %>% do.call(rbind, .) %>% as.data.frame()
  colnames(temp_file) <- c("hostname", "rule", "time", "status")
  temp_file$rule <- temp_file$rule %>% str_extract("sawfish (discover|call)")
  temp_collapsed <- lapply(temp_file$rule %>% u, function(x){
    temp_rule <- temp_file[temp_file$rule == x, ]
    if(nrow(temp_rule) == 1){return()}
    if(x != "bgzip tabix"){
      if(sum(temp_rule$status == "finish") != 1){print(file); return()}
      if(sum(temp_rule$status == "start") != 1){print(file)}  
    }
    end = temp_rule$time[temp_rule$status=="finish"]   %>% str_extract("(Jul|Apr)[[:space:]]+[0-9]+ ..:..:..") %>%  as.POSIXct(format="%b %d %H:%M:%OS")
    starts = temp_rule$time[temp_rule$status=="start"] %>% str_extract("(Jul|Apr)[[:space:]]+[0-9]+ ..:..:..") %>%  as.POSIXct(format="%b %d %H:%M:%OS")
    end <- end[length(end)]
    diff <- min(as.numeric(end - starts,units="secs"))[1] %>% abs
    rval <- data.frame(hostname = temp_rule$hostname[1] %>% str_remove(".grid.gs.washington.edu"),
               rule = temp_rule$rule[1], 
               diff = diff,
               src = file,
               stringsAsFactors = FALSE)
    return(rval)
  }) %>% do.call(rbind, .)
  return(temp_collapsed)
  
}) %>% do.call(rbind, .)
df00$src <- NULL

my_order <- c(paste0("e", c(217:226, 227:245, 246:247, 248:260, paste0("00", 1:9), paste0("0", 10:16), paste0("0", 17:22))))
my_order[grepl("e[a-z].", my_order)] <- my_order[grepl("e[a-z].", my_order)] %>% str_remove("^e")
my_age <- c(rep("2012", length(217:226)), 
            rep("2015", length(227:245)), 
            rep("2016", length(246:247)), 
            rep("2018", length(248:260)), 
            rep("2023", length(paste0("00", 1:9))), 
            rep("2023", length(paste0("0", 10:16))), 
            rep("2025", length(paste0("0", 17:22))))
df_block <- data.frame(order = my_order, 
                       age = my_age, 
                       stringsAsFactors = FALSE)


my_legend_order <- c("pbsv discover --tandem-repeats", "pbsv call DUP", "pbsv call DEL,INS,INV", "pbsv call BND")
df01 <- lapply(my_order, function(hostname){
  if(hostname %in% df00$hostname == FALSE){return()}
  
  temp_rules <- df00$rule[df00$hostname == hostname] %>% u
  collapsed_rval <- lapply(temp_rules, function(rule){
    temp_df <- df00[df00$hostname == hostname & df00$rule == rule, ]
    corrected_values <- temp_df$diff * 1
    rval <- data.frame(hostname = hostname, 
                       rule = rule,
                       mean = mean(corrected_values), 
                       sd = sd(corrected_values), 
                       n = nrow(temp_df),
                       age = df_block$age[df_block$order == temp_df$hostname[1]],
                       ID = which(my_order == hostname),
                       stringsAsFactors = FALSE)
    rval$se <- 2.6 * rval$sd / sqrt(rval$n)
    return(rval)
  }) %>% do.call(rbind, .)
  collapsed_rval <- collapsed_rval[order(match(collapsed_rval$rule, my_legend_order)), ]
  collapsed_rval$cummean <- collapsed_rval$mean %>% cumsum
  
  return(collapsed_rval)
}) %>% do.call(rbind, .)

df01$mID <- lapply(df01$hostname, function(x){
  which(u(df01$hostname) == x)
}) %>% unlist

my_ys <- c(seq(0,60000, 3600), seq(72000, 93600, 3600))

df_block2 <- df_block[df_block$order %in% df01$hostname, ]
df_vlines <- data.frame(hostname = df_block2$age %>% u, 
                        x_val = (df_block2$age %>% table %>% cumsum %>% unname) + 0.5, 
                        y_val = 3*3600)
df_vlines$x_lab <- lapply(seq_down(df_vlines), function(x){
  if(x == 1){
    a <- 0
  } else{
    a = df_vlines$x_val[x-1]
  }
  b = df_vlines$x_val[x]
  return((a+b)/2)
}) %>% unlist

df01[is.na(df01)] <- 1

# df01$lab <- paste0(round(df01$mean/3600, 1), "\n", "(",  df01$n, ")")
df01$lab <- df01$n

g3 <- ggplot(df01) + 
  geom_bar( aes(x=mID, y=mean, fill=rule), stat="identity", alpha=0.7) +
  geom_errorbar( aes(x=mID, ymin=cummean-se, ymax=cummean+se), width=0.4, colour="orange", alpha=0.9, linewidth=1.3) + 
  scale_x_continuous(breaks = df01$mID, labels = df01$hostname) +
  scale_y_continuous(breaks = my_ys, labels = my_ys/3600) + 
  geom_text(data=df01, aes(label=lab, x=mID, y=mean), size = 3, position = position_stack(vjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  xlab("hostname") + 
  ylab("time (hours)") + 
  geom_vline(data = df_vlines, aes(xintercept = x_val), linetype="dotdash", lwd=2) + 
  geom_text(data=df_vlines, aes(label=hostname, x=x_lab, y=y_val), fontface = "bold") +
  ggtitle("time to run sawfish") + 
  scale_fill_discrete(name = "Rule")
g3 

g4 <- ggplot(df01) + 
  geom_bar( aes(x=mID, y=n, fill=rule), stat="identity", alpha=0.7) +
  scale_x_continuous(breaks = df01$mID, labels = df01$hostname) +
  # scale_y_continuous(breaks = my_ys, labels = my_ys/3600) + 
  geom_text(data=df01, aes(label=lab, x=mID, y=n), size = 3, position = position_stack(vjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  xlab("hostname") + 
  ylab("count") + 
  geom_vline(data = df_vlines, aes(xintercept = x_val), linetype="dotdash", lwd=2) + 
  geom_text(data=df_vlines, aes(label=hostname, x=x_lab, y=250), fontface = "bold") +
  ggtitle("jobs run per node, sawfish") + 
  scale_fill_discrete(name = "Rule")
g4

df02 <- df00
df02$diff_log <- df02$diff %>% log
df_block2 <- df_block[df_block$order %in% df02$hostname, ]
df02$mID <- df02$hostname %>% lapply(function(x){which(df_block2$order==x)}) %>% unlist
df02 <- df02[order(df02$mID), ]

df_vlines <- data.frame(hostname = df_block2$age %>% u, 
                        x_val = (df_block2$age %>% table %>% cumsum %>% unname) + 0.5, 
                        y_val = 3*3600)
df_vlines$x_lab <- lapply(seq_down(df_vlines), function(x){
  if(x == 1){
    a <- 0
  } else{
    a = df_vlines$x_val[x-1]
  }
  b = df_vlines$x_val[x]
  return((a+b)/2)
}) %>% unlist

gg_color_hue <- function(n) {hues = seq(15, 375, length = n + 1); hcl(h = hues, l = 65, c = 100)[1:n]}
my_colors <- gg_color_hue(lu(df01$rule))
names(my_colors) <- u(df01$rule)
df02$mycol <- df02$rule %>% lapply(function(x){my_colors[x]}) %>% unlist
df02$super_group <- paste0(df02$hostname, "__", df02$rule)

my_time_breaks <- c(10, 30, 60, 5*60, 10*60, 30*60, 3600 * (1:4))
my_labels <- c("10s", "30s", "1m", "5m", "10m", "30m", paste0(1:4, "hr"))

g6 <- ggplot(df02) + 
  geom_boxplot(data=df02, aes(x=mID, y = diff_log , group=super_group), alpha = 0.5, outlier.shape = NA) +
  geom_jitter(data=df02, aes(x = mID, y = diff_log, colour = rule), width = 0.25, height = 0.05, alpha=0.8) +
  scale_x_continuous(breaks = df02$mID %>% u, labels = df02$hostname %>% u) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  xlab("hostname") +
  geom_vline(data = df_vlines, aes(xintercept = x_val), linetype="dotdash", lwd=2) + 
  geom_text(data=df_vlines, aes(label=hostname, x=x_lab, y=8.2), fontface = "bold") +
  ggtitle("sawfish runtime") +
  guides(colour = guide_legend(override.aes = list(size=10, shape=15))) +
  scale_y_continuous(breaks = log(my_time_breaks), labels=my_labels) +
  ylab("runtime")
g6
```

ls -lh ../results | awk '{print $9}' | xargs -I {} mkdir -p {}
find ../results | grep log.txt | awk -F "/" '{print "cp " $0 " " $3 "/" $4 }' | /bin/bash


cut ../manifest.tsv -f1 | grep ^f | xargs -I {} mkdir -p {}


output_log="results/{sample}/log.txt",

set -eux; mkdir -p results/{wildcards.sample}; touch {output.output_log}
echo $(hostname) "; pbsv discover --tandem-repeats; " $(date) "; start" >> {output.output_log}


```{r}
files <- list.files("C:/docs/lab_meeting_presentation_2/curve/n40/", full.names = TRUE)
df0 <- data.frame(sample = files %>% bname %>% str_remove("_hap..n50.stats") %>% u)
df0$hap1_n50 <- df0$sample %>% lapply(function(x){
  temp1 <- readLines(files[grepl(paste0(x, "_hap1"), files)])
  temp1[grepl("N50", temp1)] %>% str_extract("(?<=N50 \\(Mbp\\):).*") %>% str_trim()
}) %>% unlist
df0$hap2_n50 <- df0$sample %>% lapply(function(x){
  temp1 <- readLines(files[grepl(paste0(x, "_hap2"), files)])
  temp1[grepl("N50", temp1)] %>% str_extract("(?<=N50 \\(Mbp\\):).*") %>% str_trim()
}) %>% unlist

df1 <- fread("C:/docs/lab_meeting_presentation_2/curve/n40/qv_values.tsv") %>% as.data.frame()
colnames(df1) <- c("sample", "hap1_qv", "hap2_qv")

df2 <- merge(df0, df1, all=TRUE)
df2$hap1_n50[1:3] <- c(45.63, 44.74, 42.11)
df2$hap2_n50[1:3] <- c(46.21, 43.54, 43.43)


df3 <- fread("C:/docs/lab_meeting_presentation_2/curve/n40/summary_n50.tsv") %>% as.data.frame()
df3 <- df3[, c("sample", "n50_hap1", "n50_hap2")]
colnames(df3) <- c("sample", "hap1_n50", "hap2_n50")
df4 <- fread("C:/docs/lab_meeting_presentation_2/curve/n40/summary_qv.tsv") %>% as.data.frame()
df4 <- df4[, c("sample", "qv_hap1", "qv_hap2")]
colnames(df4) <- c("sample", "hap1_qv", "hap2_qv")
df5 <- merge(df3, df4)
df6 <- rbind(df2, df5)

df6$family <- df6$sample %>% str_remove("_.*")
df6$family[grepl("-", df6$sample)] <- "Rett like"

df6$hap1_n50 <- as.numeric(df6$hap1_n50)
df6$hap2_n50 <- as.numeric(df6$hap2_n50)

g1 <- ggplot(df6, aes(x=hap1_n50, y=hap1_qv)) + 
  geom_point(aes(color=family )) + 
  ggtitle("Hap1 HiFi Assembly") + 
  xlab("Contig N50 (Mbp)") + 
  ylab("Quality Value (Merqury)") +
  scale_x_continuous(breaks=seq(0,100,10), labels =seq(0,100,10))
g1

g2 <- ggplot(df6, aes(x=hap2_n50, y=hap2_qv)) + 
  geom_point(aes(color=family )) + 
  ggtitle("Hap2 HiFi Assembly") + 
  xlab("Contig N50 (Mbp)") + 
  ylab("Quality Value (Merqury)")+
  scale_x_continuous(breaks=seq(0,100,10), labels =seq(0,100,10))
g2
```



```{r}
df0 <- readLines("C:/docs/temp/logs.txt")
sizes <- df0 %>% str_extract("(?<=[:blank:])[0-9\\.]*(T|G)$")
dates <- df0 %>% str_extract("Apr[[:space:]]+[0-9]+ ..:..:..") %>%  as.POSIXct(format="%b %d %H:%M:%OS")
sizes_gb <- sizes %>% str_replace("T", "00") %>% str_remove("[\\.G]") %>% as.numeric()

df1 <- data.frame(time = dates, free_space = sizes_gb, stringsAsFactors = FALSE)

g1 <- ggplot(df1, aes(x=time, y=free_space)) + 
  geom_line() + 
  ggtitle("Free space available") + 
  xlab("time") +
  ylab("Free Space (GB)")
g1  
```






```{r}
files <- list.files("C:/docs/benchmark/pbsv/20250113/", recursive = TRUE, full.names = TRUE, pattern="log")

df00 <- lapply(files, function(file){
  temp_file <- readLines(file) %>% str_split(";") %>% lapply(str_trim) %>% do.call(rbind, .) %>% as.data.frame()
  colnames(temp_file) <- c("hostname", "rule", "time", "status")
  temp_collapsed <- lapply(temp_file$rule %>% u, function(x){
    temp_rule <- temp_file[temp_file$rule == x, ]
    if(nrow(temp_rule) == 1){return()}
    if(x != "bgzip tabix"){
      if(sum(temp_rule$status == "finish") != 1){return()}
      # if(sum(temp_rule$status == "start") != 1){print(file)}  
    }
    end = temp_rule$time[temp_rule$status=="finish"]   %>% str_extract("...[[:space:]]+[0-9]+ ..:..:..") %>%  as.POSIXct(format="%b %d %H:%M:%OS")
    starts = temp_rule$time[temp_rule$status=="start"] %>% str_extract("...[[:space:]]+[0-9]+ ..:..:..") %>%  as.POSIXct(format="%b %d %H:%M:%OS")
    end <- end[length(end)]
    diff <- min(as.numeric(end - starts,units="secs"))[1] %>% abs
    rval <- data.frame(hostname = temp_rule$hostname[1] %>% str_remove(".grid.gs.washington.edu"),
               rule = temp_rule$rule[1], 
               diff = diff,
               src = file,
               stringsAsFactors = FALSE)
    return(rval)
  }) %>% do.call(rbind, .)
  return(temp_collapsed)
  
}) %>% do.call(rbind, .)
df00$src <- NULL

my_order <- c(paste0("e", c(217:226, 227:245, 246:247, 248:260, paste0("00", 1:9), paste0("0", 10:16), paste0("0", 17:22), paste0("0", 23:29))))
my_order[grepl("e[a-z].", my_order)] <- my_order[grepl("e[a-z].", my_order)] %>% str_remove("^e")
my_age <- c(rep("2012", length(217:226)), 
            rep("2015", length(227:245)), 
            rep("2016", length(246:247)), 
            rep("2018", length(248:260)), 
            rep("2023", length(paste0("00", 1:9))), 
            rep("2023", length(paste0("0", 10:16))), 
            rep("2025", length(paste0("0", 17:22))),
            rep("2025", length(paste0("0", 23:29))))
df_block <- data.frame(order = my_order, 
                       age = my_age, 
                       stringsAsFactors = FALSE)


my_legend_order <- c("pbsv discover --tandem-repeats", "pbsv call DUP", "pbsv call DEL,INS,INV", "pbsv call BND")
df01 <- lapply(my_order, function(hostname){
  if(hostname %in% df00$hostname == FALSE){return()}
  
  temp_rules <- df00$rule[df00$hostname == hostname] %>% u
  collapsed_rval <- lapply(temp_rules, function(rule){
    temp_df <- df00[df00$hostname == hostname & df00$rule == rule, ]
    corrected_values <- temp_df$diff * 1
    rval <- data.frame(hostname = hostname, 
                       rule = rule,
                       mean = mean(corrected_values), 
                       sd = sd(corrected_values), 
                       n = nrow(temp_df),
                       age = df_block$age[df_block$order == temp_df$hostname[1]],
                       ID = which(my_order == hostname),
                       stringsAsFactors = FALSE)
    rval$se <- 2.6 * rval$sd / sqrt(rval$n)
    return(rval)
  }) %>% do.call(rbind, .)
  collapsed_rval <- collapsed_rval[order(match(collapsed_rval$rule, my_legend_order)), ]
  collapsed_rval$cummean <- collapsed_rval$mean %>% cumsum
  
  return(collapsed_rval)
}) %>% do.call(rbind, .)

df01$mID <- lapply(df01$hostname, function(x){
  which(u(df01$hostname) == x)
}) %>% unlist

my_ys <- c(seq(0,60000, 3600), seq(72000, 93600, 3600))

df_block2 <- df_block[df_block$order %in% df01$hostname, ]
df_vlines <- data.frame(hostname = df_block2$age %>% u, 
                        x_val = (df_block2$age %>% table %>% cumsum %>% unname) + 0.5, 
                        y_val = 3*3600)
df_vlines$x_lab <- lapply(seq_down(df_vlines), function(x){
  if(x == 1){
    a <- 0
  } else{
    a = df_vlines$x_val[x-1]
  }
  b = df_vlines$x_val[x]
  return((a+b)/2)
}) %>% unlist

df01[is.na(df01)] <- 1

# df01$lab <- paste0(round(df01$mean/3600, 1), "\n", "(",  df01$n, ")")
df01$lab <- df01$n

g3 <- ggplot(df01) + 
  geom_bar( aes(x=mID, y=mean, fill=rule), stat="identity", alpha=0.7) +
  geom_errorbar( aes(x=mID, ymin=cummean-se, ymax=cummean+se), width=0.4, colour="orange", alpha=0.9, linewidth=1.3) + 
  scale_x_continuous(breaks = df01$mID, labels = df01$hostname) +
  scale_y_continuous(breaks = my_ys, labels = my_ys/3600) + 
  geom_text(data=df01, aes(label=lab, x=mID, y=mean), size = 3, position = position_stack(vjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  xlab("hostname") + 
  ylab("time (hours)") + 
  geom_vline(data = df_vlines, aes(xintercept = x_val), linetype="dotdash", lwd=2) + 
  geom_text(data=df_vlines, aes(label=hostname, x=x_lab, y=y_val), fontface = "bold") +
  ggtitle("time to run PBSV") + 
  scale_fill_discrete(name = "Rule")
g3 

g4 <- ggplot(df01) + 
  geom_bar( aes(x=mID, y=n, fill=rule), stat="identity", alpha=0.7) +
  scale_x_continuous(breaks = df01$mID, labels = df01$hostname) +
  # scale_y_continuous(breaks = my_ys, labels = my_ys/3600) + 
  geom_text(data=df01, aes(label=lab, x=mID, y=n), size = 3, position = position_stack(vjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  xlab("hostname") + 
  ylab("count") + 
  geom_vline(data = df_vlines, aes(xintercept = x_val), linetype="dotdash", lwd=2) + 
  geom_text(data=df_vlines, aes(label=hostname, x=x_lab, y=250), fontface = "bold") +
  ggtitle("jobs run per node, PBSV") + 
  scale_fill_discrete(name = "Rule")
g4

df02 <- df00
df02$diff_log <- df02$diff %>% log
df_block2 <- df_block[df_block$order %in% df02$hostname, ]
df02$mID <- df02$hostname %>% lapply(function(x){which(df_block2$order==x)}) %>% unlist
df02 <- df02[order(df02$mID), ]

df_vlines <- data.frame(hostname = df_block2$age %>% u, 
                        x_val = (df_block2$age %>% table %>% cumsum %>% unname) + 0.5, 
                        y_val = 3*3600)
df_vlines$x_lab <- lapply(seq_down(df_vlines), function(x){
  if(x == 1){
    a <- 0
  } else{
    a = df_vlines$x_val[x-1]
  }
  b = df_vlines$x_val[x]
  return((a+b)/2)
}) %>% unlist

gg_color_hue <- function(n) {hues = seq(15, 375, length = n + 1); hcl(h = hues, l = 65, c = 100)[1:n]}
my_colors <- gg_color_hue(lu(df01$rule))
names(my_colors) <- u(df01$rule)
df02$mycol <- df02$rule %>% lapply(function(x){my_colors[x]}) %>% unlist
df02$super_group <- paste0(df02$hostname, "__", df02$rule)

my_time_breaks <- c(10, 30, 60, 5*60, 10*60, 30*60, 3600 * (1:4))
my_labels <- c("10s", "30s", "1m", "5m", "10m", "30m", paste0(1:4, "hr"))

g6 <- ggplot(df02) + 
  geom_boxplot(data=df02, aes(x=mID, y = diff_log , group=super_group), alpha = 0.5, outlier.shape = NA) +
  geom_jitter(data=df02, aes(x = mID, y = diff_log, colour = rule), width = 0.25, height = 0.05, alpha=0.8) +
  scale_x_continuous(breaks = df02$mID %>% u, labels = df02$hostname %>% u) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  xlab("hostname") +
  geom_vline(data = df_vlines, aes(xintercept = x_val), linetype="dotdash", lwd=2) + 
  geom_text(data=df_vlines, aes(label=hostname, x=x_lab, y=8.2), fontface = "bold") +
  ggtitle("PBSV runtime") +
  guides(colour = guide_legend(override.aes = list(size=10, shape=15))) +
  scale_y_continuous(breaks = log(my_time_breaks), labels=my_labels) +
  ylab("runtime")
g6
```
