---
title: "Untitled"
output: html_document
date: "2024-08-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
MAIN_PATH_1 <- "C:/Users/iwong1/Documents/mike/my_spotify_data_trisha2/"
MAIN_PATH_2 <- "C:/docs/mike/my_spotify_data_trisha2/Spotify Extended Streaming History/"
FILTER <- FALSE
library(jsonlite)
library(plyr)
library(wesanderson)
```


# get this year's top artists and tracks
```{r}
OUT_DIR <- MAIN_PATH_1
N_TOP_ARTIST <- 10
gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}
my_rev <- function(my_seq){
  temp1 <- my_seq
  if(length(my_seq)%%2==0){
    temp1[seq(1, length(my_seq), 2)] <- my_seq[seq(length(my_seq)-1, 1, -2)]
  } else {
    temp1[seq(1, length(my_seq), 2)] <- my_seq[seq(length(my_seq), 1, -2)]
  }
  return(temp1)
}
files <- list.files(MAIN_PATH_2, pattern = "json", full.names = TRUE)

df0 <- lapply(files, function(x){read_json(x)}) %>% do.call(c, .)
df1 <- do.call(rbind, df0) %>% as.data.frame()

trackToTime <- HashMap$new()
trackToLength <- HashMap$new()
artistToMonthToTime <- HashMap$new()

temp1 <- lapply(seq_along(df0), function(x){
  if(!grepl("^2025", df0[[x]]$ts)){return(-1)}
  curr_track <- df0[[x]]$master_metadata_track_name
  if(is.null(curr_track)){return(x)}

  if(trackToTime$containsKey(curr_track)){
    trackToTime$put(curr_track, trackToTime$get(curr_track) + df0[[x]]$ms_played)
  } else {
    trackToTime$put(curr_track, df0[[x]]$ms_played)
  }
  
  if(trackToLength$containsKey(curr_track)){
    trackToLength$put(curr_track, max(df0[[x]]$ms_played, trackToLength$get(curr_track)))
  } else {
    trackToLength$put(curr_track, df0[[x]]$ms_played)    
  }
  
  
  return(0)
}) %>% unlist
temp1 <- trackToTime$toString()

df2 <- data.frame(track = temp1 %>% names(),
                  time = unname(unlist(temp1)) / 3600000)
df2 <- df2[order(df2$time, decreasing = TRUE), ]
dft <- df2

artistToTime <- HashMap$new()
temp1 <- lapply(seq_along(df0), function(x){
  if(!grepl("^2025", df0[[x]]$ts)){return(-1)}
  curr_artist <- df0[[x]]$master_metadata_album_artist_name
  if(is.null(curr_artist)){return(x)}
  # print(paste0(x, " ", curr_artist))
  if(artistToTime$containsKey(curr_artist)){
    artistToTime$put(curr_artist, artistToTime$get(curr_artist) + df0[[x]]$ms_played)
  } else {
    artistToTime$put(curr_artist, df0[[x]]$ms_played)
  }
  return(0)
}) %>% unlist
temp1 <- artistToTime$toString()

df2 <- data.frame(artist = temp1 %>% names(),
                  time = unname(unlist(temp1)) / 3600000)
df2 <- df2[order(df2$time, decreasing = TRUE), ]
dfa <- df2

trackToArtist <- HashMap$new()
temp1 <- lapply(seq_along(df0), function(x){
  curr_track <- df0[[x]]$master_metadata_track_name
  if(is.null(curr_track)){return(x)}
  trackToArtist$append(curr_track, df0[[x]]$master_metadata_album_artist_name)
  return(0)
}) %>% unlist

dft$artist <- lapply(dft$track, function(x){names(srt(trackToArtist$get(x)))[1]}) %>% unlist

dfa$ID <- seq_down(dfa)


albumToTime <- HashMap$new()
temp1 <- lapply(seq_along(df0), function(x){
  if(!grepl("^2025", df0[[x]]$ts)){return(-1)}
  curr_album <- df0[[x]]$master_metadata_album_album_name
  if(is.null(curr_album)){return(x)}
  if(albumToTime$containsKey(curr_album)){
    albumToTime$put(curr_album, albumToTime$get(curr_album) + df0[[x]]$ms_played)
  } else {
    albumToTime$put(curr_album, df0[[x]]$ms_played)
  }
  return(0)
}) %>% unlist
temp1 <- albumToTime$toString()

df2 <- data.frame(album = temp1 %>% names(),
                  time = unname(unlist(temp1)) / 3600000)
df2 <- df2[order(df2$time, decreasing = TRUE), ]
dfb <- df2


g1 <- ggplot(dfa[1:N_TOP_ARTIST, ], aes(x=ID, y=time, fill=artist)) + 
  geom_bar(position="stack", stat="identity") +
  scale_x_continuous(breaks=1:N_TOP_ARTIST, labels=dfa$artist[1:N_TOP_ARTIST]) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), legend.position="none") + 
  xlab("") + 
  ylab("Hours Listened") +
  ggtitle(paste0("Spotify top ", N_TOP_ARTIST, " Artists, 2025")) +
  scale_fill_manual(name = "Artist", values = gg_color_hue(N_TOP_ARTIST) %>% my_rev) + 
  scale_y_continuous(breaks=seq(0, dfa$time[1]+50, 5))
plot(g1)
if(!FILTER)ggsave(paste0(OUT_DIR, "top_artists_202511.pdf"), g1, width = 10, height = 7, units = "in", limitsize = FALSE)
```
ggplot(df_filtered, aes(fill=master_metadata_album_artist_name, y=hour, x = rowID, label = master_metadata_album_artist_name)) + 
    geom_bar(position="stack", stat="identity") +
    scale_x_continuous(breaks = df_filtered$rowID %>% u, labels = month.name[df_filtered$rowID %>% u]) + 
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
    geom_text(size = 3, position = position_stack(vjust = 0.5)) +
    xlab("") + 
    ylab("Hours Listened") + 
    ggtitle(paste0("Spotify top ", TOP_N_ARTIST, " artists by month, ", this_year)) + 
    scale_fill_manual(name = "Artist", values = gg_color_hue(df_filtered$master_metadata_album_artist_name %>% lu) %>% my_rev) + 
    scale_y_continuous(breaks=seq(0, max_hours, 25))





# get top artists and track, lifetime
```{r}
files <- list.files(MAIN_PATH_2, pattern = "json", full.names = TRUE)

df0 <- lapply(files, function(x){read_json(x)}) %>% do.call(c, .)
df1 <- do.call(rbind, df0) %>% as.data.frame()

trackToTime <- HashMap$new()
temp1 <- lapply(seq_along(df0), function(x){
  curr_track <- df0[[x]]$master_metadata_track_name
  if(is.null(curr_track)){return(x)}
  # print(paste0(x, " ", curr_track))
  if(trackToTime$containsKey(curr_track)){
    trackToTime$put(curr_track, trackToTime$get(curr_track) + df0[[x]]$ms_played)
  } else {
    trackToTime$put(curr_track, df0[[x]]$ms_played)
  }
  return(0)
}) %>% unlist
temp2 <- df1[temp1[temp1!=0], ]
temp1 <- trackToTime$toString()

df2 <- data.frame(track = temp1 %>% names(),
                  time = unname(unlist(temp1)) / 3600000)
df2 <- df2[order(df2$time, decreasing = TRUE), ]
dft0 <- df2

trackToArtist <- HashMap$new()
temp1 <- lapply(seq_along(df0), function(x){
  curr_track <- df0[[x]]$master_metadata_track_name
  if(is.null(curr_track)){return(x)}
  trackToArtist$append(curr_track, df0[[x]]$master_metadata_album_artist_name)
  return(0)
}) %>% unlist
dft0$artist <- lapply(dft0$track, function(x){names(srt(trackToArtist$get(x)))[1]}) %>% unlist
dft0$ID <- seq_down(dft0)

artistToTime <- HashMap$new()
temp1 <- lapply(seq_along(df0), function(x){
  curr_artist <- df0[[x]]$master_metadata_album_artist_name
  if(is.null(curr_artist)){return(x)}
  # print(paste0(x, " ", curr_artist))
  if(artistToTime$containsKey(curr_artist)){
    artistToTime$put(curr_artist, artistToTime$get(curr_artist) + df0[[x]]$ms_played/1000)
  } else {
    artistToTime$put(curr_artist, df0[[x]]$ms_played/1000)
  }
  return(0)
}) %>% unlist
temp2 <- df1[temp1[temp1!=0], ]
temp1 <- artistToTime$toString()

df2 <- data.frame(artist = temp1 %>% names(),
                  time = unname(unlist(temp1)) / 3600)
df2 <- df2[order(df2$time, decreasing = TRUE), ]
dfa0 <- df2

dfa0$ID <- seq_down(dfa0)


albumToTime <- HashMap$new()
temp1 <- lapply(seq_along(df0), function(x){
  curr_album <- df0[[x]]$master_metadata_album_album_name
  if(is.null(curr_album)){return(x)}
  if(albumToTime$containsKey(curr_album)){
    albumToTime$put(curr_album, albumToTime$get(curr_album) + df0[[x]]$ms_played)
  } else {
    albumToTime$put(curr_album, df0[[x]]$ms_played)
  }
  return(0)
}) %>% unlist
temp1 <- albumToTime$toString()

df2 <- data.frame(album = temp1 %>% names(),
                  time = unname(unlist(temp1)) / 3600000)
df2 <- df2[order(df2$time, decreasing = TRUE), ]
dfb0 <- df2
dfb0$ID <- seq_down(dfb0)


N_TOP_ARTIST <- 40
g1 <- ggplot(dfa0[1:N_TOP_ARTIST, ], aes(x=ID, y=time, fill=artist)) + 
  geom_bar(position="stack", stat="identity") +
  scale_x_continuous(breaks=1:N_TOP_ARTIST, labels=dfa0$artist[1:N_TOP_ARTIST]) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), legend.position="none") + 
  xlab("") + 
  ylab("Hours Listened") +
  ggtitle(paste0("Spotify Top ", N_TOP_ARTIST, " Artists, lifetime")) +
  scale_fill_manual(name = "Artist", values = gg_color_hue(N_TOP_ARTIST) %>% my_rev) + 
  scale_y_continuous(breaks=seq(0, dfa0$time[1]+100, 10))
plot(g1)
if(!FILTER)ggsave(paste0(OUT_DIR, "top_artists_lifetime.pdf"), g1, width = 10, height = 7, units = "in", limitsize = FALSE)


N_TOP_ARTIST <- 40
g1a <- ggplot(dft0[1:N_TOP_ARTIST, ], aes(x=ID, y=time, fill=track )) + 
  geom_bar(position="stack", stat="identity") +
  scale_x_continuous(breaks=1:N_TOP_ARTIST, labels=dft0$track[1:N_TOP_ARTIST]) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), legend.position="none") + 
  xlab("") + 
  ylab("Hours Listened") +
  ggtitle(paste0("Spotify Top ", N_TOP_ARTIST, " Songs, lifetime")) +
  scale_fill_manual(name = "Song", values = gg_color_hue(N_TOP_ARTIST) %>% my_rev) + 
  scale_y_continuous(breaks=seq(0, dft0$time[1]+2, 10))
plot(g1a)
if(!FILTER)ggsave(paste0(OUT_DIR, "top_songs_lifetime.pdf"), g1a, width = 20, height = 7, units = "in", limitsize = FALSE)


N_TOP_ARTIST <- 30
g1b <- ggplot(dfb0[1:N_TOP_ARTIST, ], aes(x=ID, y=time, fill=album)) + 
  geom_bar(position="stack", stat="identity") +
  scale_x_continuous(breaks=1:N_TOP_ARTIST, labels=dfb0$album[1:N_TOP_ARTIST]) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), legend.position="none") + 
  xlab("") + 
  ylab("Hours Listened") +
  ggtitle(paste0("Spotify Top ", N_TOP_ARTIST, " Artists, lifetime")) +
  scale_fill_manual(name = "Album", values = gg_color_hue(N_TOP_ARTIST) %>% my_rev) + 
  scale_y_continuous(breaks=seq(0, dfb0$time[1]+50, 20))
plot(g1b)
if(!FILTER)ggsave(paste0(OUT_DIR, "top_albums_lifetime.pdf"), g1b, width = 10, height = 7, units = "in", limitsize = FALSE)
```



# updated DataFrame of raw data
```{r}
OUT_DIR <- MAIN_PATH_1
TOP_N_ARTIST <- 4
gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

my_rev <- function(my_seq){
  temp1 <- my_seq
  if(length(my_seq)%%2==0){
    temp1[seq(1, length(my_seq), 2)] <- my_seq[seq(length(my_seq)-1, 1, -2)]
  } else {
    temp1[seq(1, length(my_seq), 2)] <- my_seq[seq(length(my_seq), 1, -2)]
  }
  return(temp1)
}

files <- list.files(MAIN_PATH_2, pattern = "Audio.*json", full.names = TRUE)
df0 <- lapply(files, function(x){read_json(x)}) %>% do.call(c, .)
df1 <- do.call(rbind, df0) %>% as.data.frame()
df2 <- df0 %>% lapply(function(x){data.frame(as.list(unlist(x)), stringsAsFactors = FALSE)})
df3 <- rbind.fill(df2)
df3[is.na(df3)] <- "NA"
df3 <- df3[df3$master_metadata_album_artist_name != "NA", ]
df3$year <- df3$ts %>% str_extract("^20..(?=-)")
df3$month <- df3$ts %>% str_extract("(?<=-)..(?=-)")
df3$timecode <- paste0(df3$year, df3$month) %>% as.numeric()
df3$binID <- paste0(df3$timecode, "__", df3$master_metadata_album_artist_name)
df3$ms_played <- df3$ms_played %>% as.numeric()

if(FILTER)df3 <- df3[df3$year %in% c("2024", "2025"), ]
```

# Plot top artists by month
```{r}
TOP_N_ARTIST <- 8
df3$binID <- paste0(df3$timecode, "__", df3$master_metadata_album_artist_name)
df_monthly <- lapply(df3$binID %>% u, function(x){
  df_temp <- df3[df3$binID == x, ]
  rval <- data.frame(master_metadata_album_artist_name = df_temp$master_metadata_album_artist_name[1],
                     year = df_temp$year[1], 
                     month = df_temp$month[1], 
                     timecode = df_temp$timecode[1],
                     binID = df_temp$binID[1],
                     time_minute = sum(df_temp$ms_played)/60000)
  return(rval)
}) %>% do.call(rbind, .)
df_monthly$hour <- df_monthly$time_minute / 60

df_condensed <- df_monthly
df_condensed <- lapply(df_monthly$timecode %>% u, function(x){
  df_temp <- df_monthly[df_monthly$timecode == x, ]
  top_artists_monthly <- df_temp$master_metadata_album_artist_name[order(df_temp$hour, decreasing = TRUE)][1:TOP_N_ARTIST]
  df_temp1 <- df_temp[df_temp$master_metadata_album_artist_name %in% top_artists_monthly, ]
  df_temp2 <- rbind(df_temp1, 
                    data.frame(master_metadata_album_artist_name = "Other", 
                               year = df_temp$year[1], 
                               month = df_temp$month[1],
                               timecode = df_temp$timecode[1],
                               binID = paste0(df_temp$timecode[1], "__Other"),
                               time_minute = sum(df_temp$time_minute[!df_temp$master_metadata_album_artist_name %in% top_artists_monthly]),
                               hour = sum(df_temp$hour[!df_temp$master_metadata_album_artist_name %in% top_artists_monthly]))) 
  df_temp2$n_artist <- df_temp$master_metadata_album_artist_name %>% lu
  df_temp2 <- df_temp2[order(df_temp2$hour, decreasing = TRUE), ]
  return(df_temp2)
}) %>% do.call(rbind, .)


my_years <- df_condensed$year %>% u %>% as.character()
my_plots <- lapply(my_years, function(this_year){
  df_filtered <- df_condensed
  df_filtered <- df_filtered[df_filtered$year == this_year, ]
  df_filtered <- df_filtered[order(df_filtered$timecode, decreasing = FALSE), ]
  timeCodeToX <- HashMap$new()
  devnull <- lapply(seq_down(df_filtered), function(x){
    curr_key <- paste0("KEY_", df_filtered$timecode[x])
    if(timeCodeToX$containsKey(curr_key) == FALSE){
      timeCodeToX$put(curr_key, timeCodeToX$size())
    }
  })
  max_hours <- lapply(df_filtered$timecode %>% u, function(x){sum(df_filtered$hour[df_filtered$timecode==x])}) %>% unlist %>% max
  df_filtered$rowID <- lapply(seq_down(df_filtered), function(x){timeCodeToX$get( paste0("KEY_", df_filtered$timecode[x]))}) %>% unlist + 1
  df_filtered$total_a_time <- lapply(df_filtered$master_metadata_album_artist_name, function(x){df_filtered$hour[df_filtered$master_metadata_album_artist_name==x] %>% sum}) %>% unlist
  df_filtered$master_metadata_album_artist_name <- reorder(df_filtered$master_metadata_album_artist_name, df_filtered$total_a_time, decreasing = FALSE)
  df_filtered$master_metadata_album_artist_name <- factor(df_filtered$master_metadata_album_artist_name, levels=levels(df_filtered$master_metadata_album_artist_name))
  g1 <- ggplot(df_filtered, aes(fill=master_metadata_album_artist_name, y=hour, x = rowID, label = master_metadata_album_artist_name)) + 
    geom_bar(position="stack", stat="identity") +
    scale_x_continuous(breaks = df_filtered$rowID %>% u, labels = month.name[df_filtered$rowID %>% u]) + 
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
    geom_text(size = 3, position = position_stack(vjust = 0.5)) +
    xlab("") + 
    ylab("Hours Listened") + 
    ggtitle(paste0("Spotify top ", TOP_N_ARTIST, " artists by month, ", this_year)) + 
    scale_fill_manual(name = "Artist", values = gg_color_hue(df_filtered$master_metadata_album_artist_name %>% lu) %>% my_rev) + 
    scale_y_continuous(breaks=seq(0, max_hours, 25))
  if(!FILTER)ggsave(paste0(OUT_DIR, "top_artists_by_month_", TOP_N_ARTIST, "_", this_year, ".pdf"), g1, width = 14, height = 8, units = "in", limitsize = FALSE)
  return(g1)
})
my_plots

```

do top 5 artists per year
```{r}
TOP_N_ARTIST <- 7
df3$binID <- paste0(df3$year, "__", df3$master_metadata_album_artist_name)
df_yearly <- lapply(df3$binID %>% u, function(x){
  df_temp <- df3[df3$binID == x, ]
  rval <- data.frame(master_metadata_album_artist_name = df_temp$master_metadata_album_artist_name[1],
                     year = df_temp$year[1], 
                     timecode = df_temp$timecode[1],
                     binID = df_temp$binID[1],
                     time_minute = sum(df_temp$ms_played)/60000)
  return(rval)
}) %>% do.call(rbind, .)
df_yearly$hour <- df_yearly$time_minute / 60

df_condensed <- df_yearly
df_condensed <- lapply(df_yearly$year %>% u, function(x){
  df_temp <- df_yearly[df_yearly$year == x, ]
  top_artists_yearly <- df_temp$master_metadata_album_artist_name[order(df_temp$hour, decreasing = TRUE)][1:TOP_N_ARTIST]
  df_temp1 <- df_temp[df_temp$master_metadata_album_artist_name %in% top_artists_yearly, ]
  return(df_temp1[order(df_temp1$hour, decreasing = TRUE), ])
}) %>% do.call(rbind, .)


df_filtered <- df_condensed
max_hours <- lapply(df_filtered$year %>% u, function(x){sum(df_filtered$hour[df_filtered$year==x])}) %>% unlist %>% max
df_filtered$total_a_time <- lapply(df_filtered$master_metadata_album_artist_name, function(x){df_filtered$hour[df_filtered$master_metadata_album_artist_name==x] %>% sum}) %>% unlist
df_filtered$master_metadata_album_artist_name <- reorder(df_filtered$master_metadata_album_artist_name, df_filtered$total_a_time, decreasing = FALSE)
df_filtered$master_metadata_album_artist_name <- factor(df_filtered$master_metadata_album_artist_name, levels=levels(df_filtered$master_metadata_album_artist_name))

g1 <- ggplot(df_filtered, aes(fill=master_metadata_album_artist_name, y=hour, x = year, label = master_metadata_album_artist_name)) + 
  geom_bar(position="stack", stat="identity") +
  # scale_x_continuous(breaks = df_filtered$rowID %>% u, labels = month.name[df_filtered$rowID %>% u]) + 
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  xlab("") + 
  ylab("Hours Listened") + 
  ggtitle(paste0("Spotify top ", TOP_N_ARTIST, " artists by year")) +
  scale_fill_manual(name = "Artist", values = gg_color_hue(df_filtered$master_metadata_album_artist_name %>% lu) %>% my_rev) + 
  scale_y_continuous(breaks=seq(0, max_hours + 200, 100))
if(!FILTER)ggsave(paste0(OUT_DIR, "top_artists_by_year_", TOP_N_ARTIST, ".pdf"), g1, width = 10, height = 10, units = "in", limitsize = FALSE)
g1
```

# plot total listening time by year o
```{r}
df_byyear <- lapply(df3$year %>% u, function(year){
  df_temp <- df3[df3$year == year, ]
  df_temp$minute <- df_temp$ms_played/60000
  data.frame(year = year, 
             time_hours = sum(df_temp$minute)/1440) %>% return()
}) %>% do.call(rbind, .)
ggplot(df_byyear, aes(x=year, y=time_hours, group=1)) + 
  geom_line() + 
  geom_point() + 
  ylab("Time (days)") + 
  xlab("Year") + 
  ggtitle("Total time by Year") + 
  scale_y_continuous(breaks=seq(0,120,10))
```


```{r}
TOP_N_ARTIST <- 12
df3$binID <- paste0(df3$timecode, "__", df3$master_metadata_album_album_name)
df_monthly <- lapply(df3$binID %>% u, function(x){
  df_temp <- df3[df3$binID == x, ]
  rval <- data.frame(master_metadata_album_album_name = df_temp$master_metadata_album_album_name[1],
                     year = df_temp$year[1], 
                     month = df_temp$month[1], 
                     timecode = df_temp$timecode[1],
                     binID = df_temp$binID[1],
                     time_minute = sum(df_temp$ms_played)/60000)
  return(rval)
}) %>% do.call(rbind, .)
df_monthly$hour <- df_monthly$time_minute / 60

df_condensed <- df_monthly
df_condensed <- lapply(df_monthly$timecode %>% u, function(x){
  df_temp <- df_monthly[df_monthly$timecode == x, ]
  top_artists_monthly <- df_temp$master_metadata_album_album_name[order(df_temp$hour, decreasing = TRUE)][1:TOP_N_ARTIST]
  df_temp1 <- df_temp[df_temp$master_metadata_album_album_name %in% top_artists_monthly, ]
  df_temp1 <- df_temp1[order(df_temp1$hour, decreasing = TRUE), ]
  return(df_temp1)
}) %>% do.call(rbind, .)


my_years <- df_condensed$year %>% u %>% as.character()
my_plots <- lapply(my_years, function(this_year){
  df_filtered <- df_condensed
  df_filtered <- df_filtered[df_filtered$year == this_year, ]
  df_filtered <- df_filtered[order(df_filtered$timecode, decreasing = FALSE), ]
  timeCodeToX <- HashMap$new()
  devnull <- lapply(seq_down(df_filtered), function(x){
    curr_key <- paste0("KEY_", df_filtered$timecode[x])
    if(timeCodeToX$containsKey(curr_key) == FALSE){
      timeCodeToX$put(curr_key, timeCodeToX$size())
    }
  })
  max_hours <- lapply(df_filtered$timecode %>% u, function(x){sum(df_filtered$hour[df_filtered$timecode==x])}) %>% unlist %>% max
  df_filtered$rowID <- lapply(seq_down(df_filtered), function(x){timeCodeToX$get( paste0("KEY_", df_filtered$timecode[x]))}) %>% unlist + 1
  df_filtered$total_a_time <- lapply(df_filtered$master_metadata_album_album_name, function(x){df_filtered$hour[df_filtered$master_metadata_album_album_name==x] %>% sum}) %>% unlist
  df_filtered$master_metadata_album_album_name <- reorder(df_filtered$master_metadata_album_album_name, df_filtered$total_a_time, decreasing = FALSE)
  df_filtered$master_metadata_album_album_name <- factor(df_filtered$master_metadata_album_album_name, levels=levels(df_filtered$master_metadata_album_album_name))
  g1 <- ggplot(df_filtered, aes(fill=master_metadata_album_album_name, y=hour, x = rowID, label = master_metadata_album_album_name)) + 
    geom_bar(position="stack", stat="identity") +
    scale_x_continuous(breaks = df_filtered$rowID %>% u, labels = month.name[df_filtered$rowID %>% u]) + 
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
    geom_text(size = 3, position = position_stack(vjust = 0.5)) +
    xlab("") + 
    ylab("Hours Listened") + 
    ggtitle(paste0("Spotify top ", TOP_N_ARTIST, " albums by month, ", this_year)) + 
    scale_fill_manual(name = "Artist", values = gg_color_hue(df_filtered$master_metadata_album_album_name %>% lu) %>% my_rev) + 
    scale_y_continuous(breaks=seq(0, max_hours, 5)) + 
    theme(legend.position="none")
  if(!FILTER)ggsave(paste0(OUT_DIR, "top_albums_by_month_", this_year, ".pdf"), g1, width = 22, height = 10, units = "in", limitsize = FALSE)
  return(g1)
})
my_plots
```




# top tracks by month?
```{r}
trackToLength <- HashMap$new()
trackToLengths <- HashMap$new()
trackToName <- HashMap$new()

temp1 <- lapply(seq_down(df3), function(x){
  curr_track <- df3$spotify_track_uri[x]
  if(is.null(curr_track)){return(x)}
  
  trackToLengths$append(curr_track, df3$ms_played[x])    
  trackToName$put(curr_track, df3$master_metadata_track_name[x])
  
  return(0)
}) %>% unlist
temp1 <- lapply(trackToLengths$keySet(), function(x){trackToLength$put(x, median(trackToLengths$get(x)))})



TOP_N_ARTIST <- 8
df3$binID <- paste0(df3$timecode, "__", df3$spotify_track_uri )
df_monthly <- lapply(df3$binID %>% u, function(x){
  df_temp <- df3[df3$binID == x, ]
  rval <- data.frame(spotify_track_uri  = df_temp$spotify_track_uri[1],
                     master_metadata_track_name = df_temp$master_metadata_track_name[1],
                     year = df_temp$year[1], 
                     month = df_temp$month[1], 
                     timecode = df_temp$timecode[1],
                     binID = df_temp$binID[1],
                     time_minute = sum(df_temp$ms_played)/60000)
  rval$n_listens <- rval$time_minute / (trackToLength$get(df_temp$spotify_track_uri[1])/60000)
  return(rval)
}) %>% do.call(rbind, .)
df_monthly$hour <- df_monthly$time_minute / 60
df_monthly$label <- paste0(df_monthly$master_metadata_track_name, " (", round(df_monthly$n_listens), ")")

df_condensed <- df_monthly
df_condensed <- lapply(df_monthly$timecode %>% u, function(x){
  df_temp <- df_monthly[df_monthly$timecode == x, ]
  top_tracks_monthly <- df_temp$spotify_track_uri[order(df_temp$hour, decreasing = TRUE)][1:TOP_N_ARTIST]
  df_temp1 <- df_temp[df_temp$spotify_track_uri  %in% top_tracks_monthly, ]
  df_temp1 <- df_temp1[order(df_temp1$hour, decreasing = TRUE), ]
  return(df_temp1)
}) %>% do.call(rbind, .)


my_years <- df_condensed$year %>% u %>% as.character()
my_plots <- lapply(my_years, function(this_year){
  df_filtered <- df_condensed
  df_filtered <- df_filtered[df_filtered$year == this_year, ]
  df_filtered <- df_filtered[order(df_filtered$timecode, decreasing = FALSE), ]
  timeCodeToX <- HashMap$new()
  devnull <- lapply(seq_down(df_filtered), function(x){
    curr_key <- paste0("KEY_", df_filtered$timecode[x])
    if(timeCodeToX$containsKey(curr_key) == FALSE){
      timeCodeToX$put(curr_key, timeCodeToX$size())
    }
  })
  max_hours <- lapply(df_filtered$timecode %>% u, function(x){sum(df_filtered$hour[df_filtered$timecode==x])}) %>% unlist %>% max
  df_filtered$rowID <- lapply(seq_down(df_filtered), function(x){timeCodeToX$get( paste0("KEY_", df_filtered$timecode[x]))}) %>% unlist + 1
  df_filtered$total_a_time <- lapply(df_filtered$spotify_track_uri , function(x){df_filtered$hour[df_filtered$spotify_track_uri ==x] %>% sum}) %>% unlist
  df_filtered$spotify_track_uri  <- reorder(df_filtered$spotify_track_uri , df_filtered$total_a_time, decreasing = FALSE)
  df_filtered$spotify_track_uri  <- factor(df_filtered$spotify_track_uri , levels=levels(df_filtered$spotify_track_uri ))
  g1 <- ggplot(df_filtered, aes(fill=spotify_track_uri , y=hour, x = rowID, label = label )) + 
    geom_bar(position="stack", stat="identity") +
    scale_x_continuous(breaks = df_filtered$rowID %>% u, labels = month.name[df_filtered$rowID %>% u]) + 
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
    geom_text(size = 3, position = position_stack(vjust = 0.5)) +
    xlab("") + 
    ylab("Hours Listened") + 
    ggtitle(paste0("Spotify top ", TOP_N_ARTIST, " Songs by month, ", this_year)) + 
    scale_fill_manual(name = "Artist", values = gg_color_hue(df_filtered$spotify_track_uri %>% lu) %>% my_rev) + 
    scale_y_continuous(breaks=seq(0, max_hours+5, 2)) +
    theme(legend.position="none")
   if(!FILTER)ggsave(paste0(OUT_DIR, "top_songs_by_month_", this_year, ".pdf"), g1, width = 14, height = 12, units = "in", limitsize = FALSE)
  return(g1)
})

my_plots
```


# top tracks by year
```{r}
trackToLength <- HashMap$new()
trackToLengths <- HashMap$new()
trackToName <- HashMap$new()

temp1 <- lapply(seq_down(df3), function(x){
  curr_track <- df3$spotify_track_uri[x]
  if(is.null(curr_track)){return(x)}
  
  trackToLengths$append(curr_track, df3$ms_played[x])    
  trackToName$put(curr_track, df3$master_metadata_track_name[x])
  
  return(0)
}) %>% unlist
temp1 <- lapply(trackToLengths$keySet(), function(x){trackToLength$put(x, median(trackToLengths$get(x)))})



TOP_N_ARTIST <- 5
df3$binID <- paste0(df3$year, "__", df3$spotify_track_uri )
df_monthly <- lapply(df3$binID %>% u, function(x){
  df_temp <- df3[df3$binID == x, ]
  rval <- data.frame(spotify_track_uri  = df_temp$spotify_track_uri[1],
                     master_metadata_track_name = df_temp$master_metadata_track_name[1],
                     year = df_temp$year[1], 
                     month = df_temp$month[1], 
                     timecode = df_temp$timecode[1],
                     binID = df_temp$binID[1],
                     time_minute = sum(df_temp$ms_played)/60000)
  rval$n_listens <- rval$time_minute / (trackToLength$get(df_temp$spotify_track_uri[1])/60000)
  return(rval)
}) %>% do.call(rbind, .)
df_monthly$hour <- df_monthly$time_minute / 60
df_monthly$label <- paste0(df_monthly$master_metadata_track_name, " (", round(df_monthly$n_listens), ")")

df_condensed <- df_monthly
df_condensed <- lapply(df_monthly$year %>% u, function(x){
  df_temp <- df_monthly[df_monthly$year == x, ]
  top_tracks_monthly <- df_temp$spotify_track_uri[order(df_temp$hour, decreasing = TRUE)][1:TOP_N_ARTIST]
  df_temp1 <- df_temp[df_temp$spotify_track_uri  %in% top_tracks_monthly, ]
  df_temp1 <- df_temp1[order(df_temp1$hour, decreasing = TRUE), ]
  return(df_temp1)
}) %>% do.call(rbind, .)

df_filtered <- df_condensed
df_filtered <- df_filtered[order(df_filtered$timecode, decreasing = FALSE), ]
timeCodeToX <- HashMap$new()
devnull <- lapply(seq_down(df_filtered), function(x){
  curr_key <- paste0("KEY_", df_filtered$timecode[x])
  if(timeCodeToX$containsKey(curr_key) == FALSE){
    timeCodeToX$put(curr_key, timeCodeToX$size())
  }
})
max_hours <- lapply(df_filtered$timecode %>% u, function(x){sum(df_filtered$hour[df_filtered$timecode==x])}) %>% unlist %>% max
df_filtered$rowID <- lapply(seq_down(df_filtered), function(x){timeCodeToX$get( paste0("KEY_", df_filtered$timecode[x]))}) %>% unlist + 1
df_filtered$total_a_time <- lapply(df_filtered$spotify_track_uri , function(x){df_filtered$hour[df_filtered$spotify_track_uri ==x] %>% sum}) %>% unlist
df_filtered$spotify_track_uri  <- reorder(df_filtered$spotify_track_uri , df_filtered$total_a_time, decreasing = FALSE)
df_filtered$spotify_track_uri  <- factor(df_filtered$spotify_track_uri , levels=levels(df_filtered$spotify_track_uri ))
g1 <- ggplot(df_filtered, aes(fill=spotify_track_uri , y=hour, x = year, label = label )) + 
  geom_bar(position="stack", stat="identity") +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  xlab("") + 
  ylab("Hours Listened") + 
  ggtitle(paste0("Spotify top ", TOP_N_ARTIST, " Songs of the year ")) + 
  scale_fill_manual(name = "Artist", values = gg_color_hue(df_filtered$spotify_track_uri %>% lu) %>% my_rev) + 
  scale_y_continuous(breaks=seq(0, max_hours+5, 25)) +
  theme(legend.position="none")
if(!FILTER)ggsave(paste0(OUT_DIR, "top_songs_by_year.pdf"), g1, width = 10, height = 8, units = "in", limitsize = FALSE)
g1
```


"US/Pacific" 


usual listening time, by minute resolution
```{r}
MY_YEAR <- df3$year %>% u

for(YEAR in MY_YEAR){
  df00 <- df3[grepl(paste0("^", YEAR), df3$ts), ]
  df00$POSIX_TIME <- as.POSIXct(df00$ts, format="%Y-%m-%dT%H:%M:%OSZ", tz="UTC")
  df00$PST <- df00$POSIX_TIME %>% format(tz="US/Pacific" ,usetz=TRUE)
  df00$timestamp_key <- df00$PST %>% str_extract("(?<=[:space:])[:digit:]{2}:[:digit:]{2}(?=:)")
  df00$minute_increment <- floor( df00$ms_played / 60000)
  # df00$stop_time <- df00$PST + floor(df00$ms_played/1000)
  
  timestamps <- expand.grid(0:59, 0:23)
  timestamps$Var1 <- sprintf("%02d", timestamps$Var1)
  timestamps$Var2 <- sprintf("%02d", timestamps$Var2)
  timestamps$key <- paste0(timestamps$Var2, ":", timestamps$Var1)
  
  timeToCount <- HashMap$new()
  for(key in timestamps$key){
    timeToCount$put(key, 0)
  }
  
  for(i in seq_down(df00)){
    my_key <- df00$timestamp_key[i]
    timeToCount$put(my_key, timeToCount$get(my_key) + 1)
    my_len <- df00$minute_increment[i]
    if(my_len > 0){
      for(k in seq(1, my_len)){
        next_key <- timestamps$key[((which(timestamps$key==my_key) + k) %% nrow(timestamps)) + 1]
        timeToCount$put(next_key, timeToCount$get(next_key) + 1)
      }
    }
  }
  
  timestamps$count <- lapply(timestamps$key, function(key){
    timeToCount$get(key)
  }) %>% unlist
  timestamps$x <- seq_down(timestamps)
  
  g1 <- ggplot(timestamps, aes(x=x, y=count)) + 
    geom_point(alpha=0.7, color=wes_palette("Darjeeling2")[2]) +
    scale_x_continuous(breaks = seq(from=1, to=1500, by=60), labels = c("12AM", paste0(1:11, "AM"), "12PM", paste0(1:11, "PM"), "12AM")) +
    ggtitle(paste0("Average Daily Listening Activity, ", YEAR)) + 
    theme(axis.text.y=element_blank(), 
          axis.ticks.y=element_blank(),
          axis.title.y=element_blank(),
          axis.title.x = element_blank())
  
  df000 <- data.frame(values= lapply(seq_down(timestamps), function(i){
    rep(timestamps$x[i], timestamps$count[i])
  }) %>% unlist)
  g2 <- ggplot(df000, aes(x=values)) + 
    geom_histogram(aes(y=..density..), fill=wes_palette("Darjeeling2")[3], binwidth=30, color=wes_palette("Moonrise2")[2]) + 
    geom_density(alpha=.2, fill=wes_palette("Moonrise2")[4]) +
    scale_x_continuous(breaks = seq(from=1, to=1500, by=60), labels = c("12AM", paste0(1:11, "AM"), "12PM", paste0(1:11, "PM"), "12AM")) +
    xlab("time") + 
    ylab("listening frequency") + 
    theme(axis.text.y=element_blank(), 
          axis.ticks.y=element_blank()) +
    ggtitle(paste0("Average Daily Listening Activity, ", YEAR)) 
  # plot(g1)
  plot(g2)
  if(!FILTER)ggsave(paste0(OUT_DIR, "average_daily_listening_activity_", YEAR, ".pdf"), g2, width = 10, height = 8, units = "in", limitsize = FALSE)
}
```



usual listening time, by second resolution
```{r}
MY_YEAR <- df3$year %>% u

my_plots <- vector("list", length = lu(MY_YEAR))
names(my_plots) <- MY_YEAR

for(YEAR in MY_YEAR){
  print(YEAR)
  df00 <- df3[grepl(paste0("^", YEAR), df3$ts), ]
  df00$POSIX_TIME <- as.POSIXct(df00$ts, format="%Y-%m-%dT%H:%M:%OSZ", tz="UTC")
  df00$PST <- df00$POSIX_TIME %>% format(tz="US/Pacific" ,usetz=TRUE)
  df00$timestamp_key <- df00$PST %>% str_extract("(?<=[:space:])[:digit:]{2}:[:digit:]{2}:[:digit:]{2}(?=[:space:])")
  df00$second_increment <- floor( df00$ms_played / 1000)
  # df00$stop_time <- df00$PST + floor(df00$ms_played/1000)
  
  timestamps <- expand.grid(0:59, 0:59, 0:23)
  timestamps$Var1 <- sprintf("%02d", timestamps$Var1)
  timestamps$Var2 <- sprintf("%02d", timestamps$Var2)
  timestamps$Var3 <- sprintf("%02d", timestamps$Var3)
  timestamps$key <- paste0(timestamps$Var3, ":", timestamps$Var2, ":", timestamps$Var1)
  
  timeToCount <- HashMap$new()
  for(key in timestamps$key){
    timeToCount$put(key, 0)
  }
  
  timestamp_key_to_index <- HashMap$new()
  for(i in seq_down(timestamps)){
    timestamp_key_to_index$put(timestamps$key[i], i)
  }
  
  timestamp_index_to_key <- HashMap$new()
  for(i in seq_down(timestamps)){
    timestamp_index_to_key$put(as.character(i), timestamps$key[i])
  }

  N_TIMESTAMPS <- nrow(timestamps)
  t1 <- Sys.time()
  for(i in seq_down(df00)){
    my_key <- df00$timestamp_key[i]
    timeToCount$put(my_key, timeToCount$get(my_key) + 1)
    my_len <- df00$second_increment[i]
    if(my_len > 0){
      for(k in seq(1, my_len)){
        next_key <- timestamp_index_to_key$get(as.character(
          ((timestamp_key_to_index$get(my_key) + k) %% N_TIMESTAMPS) + 1 
        ))
        timeToCount$put(next_key, timeToCount$get(next_key) + 1)
      }
    }
  }
  print(Sys.time() - t1)
  
  timestamps$count <- lapply(timestamps$key, function(key){
    timeToCount$get(key)
  }) %>% unlist
  timestamps$x <- seq_down(timestamps)
  
  g1 <- ggplot(timestamps, aes(x=x, y=count)) + 
    geom_jitter(alpha=0.05, color=wes_palette("Darjeeling2")[2], width = 0, height = 0.5) +
    scale_x_continuous(breaks = seq(from=1, to=90000, by=3600), labels = c("12AM", paste0(1:11, "AM"), "12PM", paste0(1:11, "PM"), "12AM")) +
    ggtitle(paste0("Average Daily Listening Activity, ", YEAR)) + 
    theme(axis.text.y=element_blank(), 
          axis.ticks.y=element_blank(),
          axis.title.y=element_blank(),
          axis.title.x = element_blank())
  plot(g1)
  my_plots[[YEAR]] <- g1
}



for(YEAR in MY_YEAR){
   if(!FILTER)ggsave(paste0(OUT_DIR, "average_listening_activity_", YEAR, ".pdf"), my_plots[[YEAR]], width = 16, height = 8, units = "in", limitsize = FALSE)
}

```

heatmap
x is month, y is day time
```{r}
N_BINS <- 24

MY_YEAR <- df3$year %>% u

for(YEAR in MY_YEAR){
  df00 <- df3[grepl(paste0("^", YEAR), df3$ts), ]
  df00$POSIX_TIME <- as.POSIXct(df00$ts, format="%Y-%m-%dT%H:%M:%OSZ", tz="UTC")
  df00$PST <- df00$POSIX_TIME %>% format(tz="US/Pacific" ,usetz=TRUE)
  df00$timestamp_key <- df00$PST %>% str_extract("(?<=[:space:])[:digit:]{2}:[:digit:]{2}(?=:)")
  df00$minute_increment <- floor( df00$ms_played / 60000)
  
  timestamps <- expand.grid(0:59, 0:23)
  timestamps$Var1 <- sprintf("%02d", timestamps$Var1)
  timestamps$Var2 <- sprintf("%02d", timestamps$Var2)
  timestamps$key <- paste0(timestamps$Var2, ":", timestamps$Var1)
  timestamps$y_time <- seq_down(timestamps)
  
  monthToTimeStamps <- HashMap$new()
  for(month in u(timestamps$Var2)){
    monthToTimeStamps$put(month, HashMap$new())
    for(key in timestamps$key){
      monthToTimeStamps$get(month)$put(key, 0)
    }  
  }

  # get counts per month per timestamp
  for(i in seq_down(df00)){
    my_month <- df00$month[i]
    my_key <- df00$timestamp_key[i]
    monthToTimeStamps$get(my_month)$put(my_key, monthToTimeStamps$get(my_month)$get(my_key) + 1)
    my_len <- df00$minute_increment[i]
    if(my_len > 0){
      for(k in seq(1, my_len)){
        next_key <- timestamps$key[((which(timestamps$key==my_key) + k) %% nrow(timestamps)) + 1]
        monthToTimeStamps$get(my_month)$put(next_key, monthToTimeStamps$get(my_month)$get(next_key) + 1)
      }
    }
  }
  
  # convert back to DF
  df_heat <- expand.grid(0:59, 0:23, seq(1, lu(df00$month)))
  df_heat$y_time <- rep(seq(1, max(timestamps$y_time)), lu(df00$month))
  df_heat$Var1 <- sprintf("%02d", df_heat$Var1)
  df_heat$Var2 <- sprintf("%02d", df_heat$Var2)
  df_heat$key <- paste0(df_heat$Var2, ":", df_heat$Var1)
  df_heat$month <- sprintf("%02d", df_heat$Var3)
  
  df_heat$count <- lapply(seq_down(df_heat), function(i){
    curr_month <- df_heat$month[i]
    curr_key <- df_heat$key[i]
     monthToTimeStamps$get(curr_month)$get(curr_key)
  }) %>% unlist
  df_heat$scaled_count <- (df_heat$count-min(df_heat$count))/(max(df_heat$count)-min(df_heat$count))
  
  bin_width <- nrow(timestamps)/N_BINS
  df_heat$small_bin <- rep(rep(seq(1, N_BINS), each=bin_width), lu(df_heat$month))
  df_heat$small_bin_key <- paste0(df_heat$month, "_", df_heat$small_bin)
  df_heat$bin_count <- lapply(seq_down(df_heat), function(i){
    sum(df_heat$count[df_heat$small_bin_key==df_heat$small_bin_key[i]])
  }) %>% unlist
  df_heat$scaled_count_bin <- (df_heat$bin_count-min(df_heat$bin_count))/(max(df_heat$bin_count)-min(df_heat$bin_count))
  df_heat$scaled_count_bin_by_month <- lapply(seq_down(df_heat), function(i){
    curr_month <- df_heat$month[i]
    min_val <- min(df_heat$bin_count[df_heat$month==curr_month])
    max_val <- max(df_heat$bin_count[df_heat$month==curr_month])
    curr_bin_val <- df_heat$bin_count[i]
    rval <- (curr_bin_val-min_val)/(max_val-min_val)
    return(rval)
  }) %>% unlist
  
  g1 <- ggplot(df_heat, aes(x=Var3, y=y_time, fill=scaled_count_bin)) + 
    geom_tile() + 
    scale_y_continuous(breaks = seq(from=1, to=1500, by=60), labels = c("12AM", paste0(1:11, "AM"), "12PM", paste0(1:11, "PM"), "12AM")) + 
    scale_x_continuous(breaks = df_heat$Var3  %>% u, labels = month.name[df_heat$Var3 %>% u]) +
    theme(axis.title.y=element_blank(), 
          axis.title.x = element_blank(),
          legend.position="none") +
    ggtitle(paste0("Listening Activity Heatmap, ", YEAR, ". scaled by year")) 
  
  g2 <- ggplot(df_heat, aes(x=Var3, y=y_time, fill=scaled_count_bin_by_month)) + 
    geom_tile() + 
    scale_y_continuous(breaks = seq(from=1, to=1500, by=60), labels = c("12AM", paste0(1:11, "AM"), "12PM", paste0(1:11, "PM"), "12AM")) + 
    scale_x_continuous(breaks = df_heat$Var3  %>% u, labels = month.name[df_heat$Var3 %>% u]) +
    theme(axis.title.y=element_blank(), 
          axis.title.x = element_blank(),
          legend.position="none") +
    ggtitle(paste0("Listening Activity Heatmap, ", YEAR, ". scaled by month")) #+ scale_fill_gradient(low = "darkblue", high = "lightskyblue1")
    
    # plot(g1)
    plot(g2)
    
    if(!FILTER)ggsave(paste0(OUT_DIR, "heatmap_listening_activity_month_", YEAR, ".pdf"), g2, width = 11, height = 9, units = "in", limitsize = FALSE)
}
```


heatmap
x is month, y is day time
```{r}
N_BINS <- 24

MY_YEAR <- df3$year %>% u

weekday_labels <- c("Sunday", "Monday", "Tuesday",  "Wednesday", "Thursday", "Friday", "Saturday")

for(YEAR in MY_YEAR){
  df00 <- df3[grepl(paste0("^", YEAR), df3$ts), ]
  df00$POSIX_TIME <- as.POSIXct(df00$ts, format="%Y-%m-%dT%H:%M:%OSZ", tz="UTC")
  df00$PST <- df00$POSIX_TIME %>% format(tz="US/Pacific" ,usetz=TRUE)
  df00$timestamp_key <- df00$PST %>% str_extract("(?<=[:space:])[:digit:]{2}:[:digit:]{2}(?=:)")
  df00$minute_increment <- floor( df00$ms_played / 60000)
  
  df00$dayoftheweek <-  weekdays(as.Date(df00$PST %>% str_extract("...-..-..")))
  
  timestamps <- expand.grid(0:59, 0:23)
  timestamps$hour <- sprintf("%02d", timestamps$Var1)
  timestamps$minute <- sprintf("%02d", timestamps$Var2)
  timestamps$key <- paste0(timestamps$minute, ":", timestamps$hour)
  timestamps$y_time <- seq_down(timestamps)
  
  weekToTimeStamps <- HashMap$new()
  for(day in weekday_labels){
    weekToTimeStamps$put(day, HashMap$new())
    for(key in timestamps$key){
      weekToTimeStamps$get(day)$put(key, 0)
    }  
  }

  # get counts per month per timestamp
  for(i in seq_down(df00)){
    my_day <- df00$dayoftheweek[i]
    my_key <- df00$timestamp_key[i]
    weekToTimeStamps$get(my_day)$put(my_key, weekToTimeStamps$get(my_day)$get(my_key) + 1)
    my_len <- df00$minute_increment[i]
    if(my_len > 0){
      for(k in seq(1, my_len)){
        next_key <- timestamps$key[((which(timestamps$key==my_key) + k) %% nrow(timestamps)) + 1]
        weekToTimeStamps$get(my_day)$put(next_key, weekToTimeStamps$get(my_day)$get(next_key) + 1)
      }
    }
  }
  
  # convert back to DF
  df_heat <- expand.grid(0:59, 0:23, seq(1, lu(df00$dayoftheweek)))
  df_heat$y_time <- rep(seq(1, max(timestamps$y_time)), lu(df00$dayoftheweek))
  df_heat$Var1 <- sprintf("%02d", df_heat$Var1)
  df_heat$Var2 <- sprintf("%02d", df_heat$Var2)
  df_heat$key <- paste0(df_heat$Var2, ":", df_heat$Var1)
  df_heat$day <- weekday_labels[df_heat$Var3]
  
  df_heat$count <- lapply(seq_down(df_heat), function(i){
    curr_day <- df_heat$day[i]
    curr_key <- df_heat$key[i]
     weekToTimeStamps$get(curr_day)$get(curr_key)
  }) %>% unlist
  df_heat$scaled_count <- (df_heat$count-min(df_heat$count))/(max(df_heat$count)-min(df_heat$count))
  
  bin_width <- nrow(timestamps)/N_BINS
  df_heat$small_bin <- rep(rep(seq(1, N_BINS), each=bin_width), lu(df_heat$day))
  df_heat$small_bin_key <- paste0(df_heat$day, "_", df_heat$small_bin)
  df_heat$bin_count <- lapply(seq_down(df_heat), function(i){
    sum(df_heat$count[df_heat$small_bin_key==df_heat$small_bin_key[i]])
  }) %>% unlist
  df_heat$scaled_count_bin <- (df_heat$bin_count-min(df_heat$bin_count))/(max(df_heat$bin_count)-min(df_heat$bin_count))
  df_heat$scaled_count_bin_by_day <- lapply(seq_down(df_heat), function(i){
    curr_day <- df_heat$day[i]
    min_val <- min(df_heat$bin_count[df_heat$day==curr_day])
    max_val <- max(df_heat$bin_count[df_heat$day==curr_day])
    curr_bin_val <- df_heat$bin_count[i]
    rval <- (curr_bin_val-min_val)/(max_val-min_val)
    return(rval)
  }) %>% unlist
  
  g1 <- ggplot(df_heat, aes(x=Var3, y=y_time, fill=scaled_count_bin)) + 
    geom_tile() + 
    scale_y_continuous(breaks = seq(from=1, to=1500, by=60), labels = c("12AM", paste0(1:11, "AM"), "12PM", paste0(1:11, "PM"), "12AM")) + 
    scale_x_continuous(breaks = df_heat$Var3  %>% u, labels = weekday_labels) +
    theme(axis.title.y=element_blank(), 
          axis.title.x = element_blank(),
          legend.position="none") +
    ggtitle(paste0("Weekly Listening Activity Heatmap, ", YEAR, ".")) 
  
  
    plot(g1)
    
    if(!FILTER)ggsave(paste0(OUT_DIR, "heatmap_listening_activity_week_", YEAR, ".pdf"), g2, width = 11, height = 9, units = "in", limitsize = FALSE)
}
```


Look at data from just the past year
# TODO: remove data from last trailing month from last year if it overlaps with the current month's most recent data
# EG: don't want data from 8/1/25-8/15/25 and 8/16/24-8/31/24 to be in the same dataset here
```{r}
OUT_DIR <- MAIN_PATH_1
TOP_N_ARTIST <- 4
gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

my_rev <- function(my_seq){
  temp1 <- my_seq
  if(length(my_seq)%%2==0){
    temp1[seq(1, length(my_seq), 2)] <- my_seq[seq(length(my_seq)-1, 1, -2)]
  } else {
    temp1[seq(1, length(my_seq), 2)] <- my_seq[seq(length(my_seq), 1, -2)]
  }
  return(temp1)
}

files <- list.files(MAIN_PATH_2, pattern = "Audio.*json", full.names = TRUE)
df0 <- lapply(files, function(x){read_json(x)}) %>% do.call(c, .)
df1 <- do.call(rbind, df0) %>% as.data.frame()
df2 <- df0 %>% lapply(function(x){data.frame(as.list(unlist(x)), stringsAsFactors = FALSE)})
df5 <- rbind.fill(df2)
df5[is.na(df5)] <- "NA"
df5 <- df5[df5$master_metadata_album_artist_name != "NA", ]
df5$year <- df5$ts %>% str_extract("^202.(?=-)")
df5$month <- df5$ts %>% str_extract("(?<=-)..(?=-)")
df5$timecode <- paste0(df5$year, df5$month) %>% as.numeric()
df5$binID <- paste0(df5$timecode, "__", df5$master_metadata_album_artist_name)
df5$ms_played <- df5$ms_played %>% as.numeric()

df5$POSIX_TIME <- as.POSIXct(df5$ts, format="%Y-%m-%dT%H:%M:%OSZ", tz="UTC")
df5$PST <- df5$POSIX_TIME %>% format(tz="US/Pacific" ,usetz=TRUE)

df5$BOOL_YEAR <- abs(df5$POSIX_TIME - as.POSIXct(Sys.time())) <= 365
df6 <- df5[df5$BOOL_YEAR, ]
df6 <- df6[order(df6$POSIX_TIME), ]

#filter data from last year's first month, which overlaps with the latest month
if(lu(df6$timecode) > 12){
  df6 <- df6[df6$timecode!=df6$timecode[1], ]  
}


artistToTime <- HashMap$new()
temp1 <- lapply(seq_down(df6), function(x){
  curr_artist <- df6$master_metadata_album_artist_name[x]
  if(is.null(curr_artist)){return(x)}
  if(artistToTime$containsKey(curr_artist)){
    artistToTime$put(curr_artist, artistToTime$get(curr_artist) + df6$ms_played[x])
  } else {
    artistToTime$put(curr_artist, df6$ms_played[x])
  }
  return(0)
}) %>% unlist
temp1 <- artistToTime$toString()
df2 <- data.frame(artist = temp1 %>% names(),
                  time = unname(unlist(temp1)) / 3600000)
df2 <- df2[order(df2$time, decreasing = TRUE), ]
dfa <- df2
dfa$ID <- seq_down(dfa)

N_TOP_ARTIST <- 40
g20 <- ggplot(dfa[1:N_TOP_ARTIST, ], aes(x=ID, y=time, fill=artist)) + 
  geom_bar(position="stack", stat="identity") +
  scale_x_continuous(breaks=1:N_TOP_ARTIST, labels=dfa$artist[1:N_TOP_ARTIST]) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), legend.position="none") + 
  xlab("") + 
  ylab("Hours Listened") +
  ggtitle(paste0("Spotify Top ", N_TOP_ARTIST, " Artists, Past Year")) +
  scale_fill_manual(name = "Artist", values = gg_color_hue(N_TOP_ARTIST) %>% my_rev) + 
  scale_y_continuous(breaks=seq(0, dfa$time[1]+100, 100))
plot(g20)

trackToTime <- HashMap$new()
idToName <- HashMap$new()
temp2 <- lapply(seq_down(df6), function(x){
  curr_track <- df6$spotify_track_uri[x]
  if(is.null(curr_track)){return(x)}
  if(trackToTime$containsKey(curr_track)){
    trackToTime$put(curr_track, trackToTime$get(curr_track) + df6$ms_played[x])
  } else {
    trackToTime$put(curr_track, df6$ms_played[x])
    idToName$put(curr_track, df6$master_metadata_track_name[x])
  }
  return(0)
}) %>% unlist
temp2 <- trackToTime$toString()
df3 <- data.frame(track = temp2 %>% names(),
                  time = unname(unlist(temp2)) / 3600000)
df3 <- df3[order(df3$time, decreasing = TRUE), ]
dft <- df3
dft$ID <- seq_down(dft)
dft$name <- lapply(dft$track, function(x){idToName$get(x)}) %>% unlist

N_TOP_ARTIST <- 40
g201 <- ggplot(dft[1:N_TOP_ARTIST, ], aes(x=ID, y=time, fill=track)) + 
  geom_bar(position="stack", stat="identity") +
  scale_x_continuous(breaks=1:N_TOP_ARTIST, labels=dft$name[1:N_TOP_ARTIST]) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), legend.position="none") + 
  xlab("") + 
  ylab("Hours Listened") +
  ggtitle(paste0("Spotify Top ", N_TOP_ARTIST, " Songs, Past Year")) +
  scale_fill_manual(name = "Artist", values = gg_color_hue(N_TOP_ARTIST) %>% my_rev) + 
  scale_y_continuous(breaks=seq(0, dft$time[1], 2))
plot(g201)

albumToTime <- HashMap$new()
temp3 <- lapply(seq_down(df6), function(x){
  curr_album <- df6$master_metadata_album_album_name[x]
  if(is.null(curr_album)){return(x)}
  if(albumToTime$containsKey(curr_album)){
    albumToTime$put(curr_album, albumToTime$get(curr_album) + df6$ms_played[x])
  } else {
    albumToTime$put(curr_album, df6$ms_played[x])
  }
  return(0)
}) %>% unlist
temp3 <- albumToTime$toString()
df3 <- data.frame(album = temp3 %>% names(),
                  time = unname(unlist(temp3)) / 3600000)
df3 <- df3[order(df3$time, decreasing = TRUE), ]
dfb <- df3
dfb$ID <- seq_down(dfb)

N_TOP_ARTIST <- 40
g202 <- ggplot(dfb[1:N_TOP_ARTIST, ], aes(x=ID, y=time, fill=album)) + 
  geom_bar(position="stack", stat="identity") +
  scale_x_continuous(breaks=1:N_TOP_ARTIST, labels=dfb$album[1:N_TOP_ARTIST]) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), legend.position="none") + 
  xlab("") + 
  ylab("Hours Listened") +
  ggtitle(paste0("Spotify Top ", N_TOP_ARTIST, " Songs, Past Year")) +
  scale_fill_manual(name = "Artist", values = gg_color_hue(N_TOP_ARTIST) %>% my_rev) + 
  scale_y_continuous(breaks=seq(0, dfb$time[1], 2))
plot(g202)
ggsave(paste0(OUT_DIR, "top_artists_past_year_", TOP_N_ARTIST, ".pdf"), g20, width = 14, height = 8, units = "in", limitsize = FALSE)
ggsave(paste0(OUT_DIR, "top_songs_past_year_", TOP_N_ARTIST, ".pdf"), g201, width = 14, height = 8, units = "in", limitsize = FALSE)
ggsave(paste0(OUT_DIR, "top_albums_past_year_", TOP_N_ARTIST, ".pdf"), g202, width = 14, height = 8, units = "in", limitsize = FALSE)
```


```{r}
TOP_N_ARTIST <- 8
df6$binID <- paste0(df6$timecode, "__", df6$master_metadata_album_artist_name)
df_monthly <- lapply(df6$binID %>% u, function(x){
  df_temp <- df6[df6$binID == x, ]
  rval <- data.frame(master_metadata_album_artist_name = df_temp$master_metadata_album_artist_name[1],
                     year = df_temp$year[1], 
                     month = df_temp$month[1], 
                     timecode = df_temp$timecode[1],
                     binID = df_temp$binID[1],
                     time_minute = sum(df_temp$ms_played)/60000)
  return(rval)
}) %>% do.call(rbind, .)
df_monthly$hour <- df_monthly$time_minute / 60

df_condensed <- df_monthly
df_condensed <- lapply(df_monthly$timecode %>% u, function(x){
  df_temp <- df_monthly[df_monthly$timecode == x, ]
  top_artists_monthly <- df_temp$master_metadata_album_artist_name[order(df_temp$hour, decreasing = TRUE)][1:TOP_N_ARTIST]
  df_temp1 <- df_temp[df_temp$master_metadata_album_artist_name %in% top_artists_monthly, ]
  df_temp2 <- rbind(df_temp1, 
                    data.frame(master_metadata_album_artist_name = "Other", 
                               year = df_temp$year[1], 
                               month = df_temp$month[1],
                               timecode = df_temp$timecode[1],
                               binID = paste0(df_temp$timecode[1], "__Other"),
                               time_minute = sum(df_temp$time_minute[!df_temp$master_metadata_album_artist_name %in% top_artists_monthly]),
                               hour = sum(df_temp$hour[!df_temp$master_metadata_album_artist_name %in% top_artists_monthly]))) 
  df_temp2$n_artist <- df_temp$master_metadata_album_artist_name %>% lu
  df_temp2 <- df_temp2[order(df_temp2$hour, decreasing = TRUE), ]
  return(df_temp2)
}) %>% do.call(rbind, .)
df_filtered <- df_condensed
df_filtered <- df_filtered[order(df_filtered$timecode, decreasing = FALSE), ]
timeCodeToX <- HashMap$new()
devnull <- lapply(seq_down(df_filtered), function(x){
  curr_key <- paste0("KEY_", df_filtered$timecode[x])
  if(timeCodeToX$containsKey(curr_key) == FALSE){
    timeCodeToX$put(curr_key, timeCodeToX$size())
  }
})
max_hours <- lapply(df_filtered$timecode %>% u, function(x){sum(df_filtered$hour[df_filtered$timecode==x])}) %>% unlist %>% max
df_filtered$rowID <- lapply(seq_down(df_filtered), function(x){timeCodeToX$get( paste0("KEY_", df_filtered$timecode[x]))}) %>% unlist + 1
df_filtered$total_a_time <- lapply(df_filtered$master_metadata_album_artist_name, function(x){df_filtered$hour[df_filtered$master_metadata_album_artist_name==x] %>% sum}) %>% unlist
df_filtered$master_metadata_album_artist_name <- reorder(df_filtered$master_metadata_album_artist_name, df_filtered$total_a_time, decreasing = FALSE)
df_filtered$master_metadata_album_artist_name <- factor(df_filtered$master_metadata_album_artist_name, levels=levels(df_filtered$master_metadata_album_artist_name))
g1 <- ggplot(df_filtered, aes(fill=master_metadata_album_artist_name, y=hour, x = rowID, label = master_metadata_album_artist_name)) + 
  geom_bar(position="stack", stat="identity") +
  scale_x_continuous(breaks = df_filtered$rowID %>% u, labels = month.name[df_filtered$month %>% u %>% as.numeric()]) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  xlab("") + 
  ylab("Hours Listened") + 
  ggtitle(paste0("Spotify top ", TOP_N_ARTIST, " artists by month, past year")) + 
  scale_fill_manual(name = "Artist", values = gg_color_hue(df_filtered$master_metadata_album_artist_name %>% lu) %>% my_rev) + 
  scale_y_continuous(breaks=seq(0, max_hours, 25))
ggsave(paste0(OUT_DIR, "top_artists_by_month_past_year_", TOP_N_ARTIST, ".pdf"), g1, width = 14, height = 8, units = "in", limitsize = FALSE)
plot(g1)
```


```{r}
TOP_N_ARTIST <- 12
df6$binID <- paste0(df6$timecode, "__", df6$master_metadata_album_album_name)
df_monthly <- lapply(df6$binID %>% u, function(x){
  df_temp <- df6[df6$binID == x, ]
  rval <- data.frame(master_metadata_album_album_name = df_temp$master_metadata_album_album_name[1],
                     year = df_temp$year[1], 
                     month = df_temp$month[1], 
                     timecode = df_temp$timecode[1],
                     binID = df_temp$binID[1],
                     time_minute = sum(df_temp$ms_played)/60000)
  return(rval)
}) %>% do.call(rbind, .)
df_monthly$hour <- df_monthly$time_minute / 60

df_condensed <- df_monthly
df_condensed <- lapply(df_monthly$timecode %>% u, function(x){
  df_temp <- df_monthly[df_monthly$timecode == x, ]
  top_artists_monthly <- df_temp$master_metadata_album_album_name[order(df_temp$hour, decreasing = TRUE)][1:TOP_N_ARTIST]
  df_temp1 <- df_temp[df_temp$master_metadata_album_album_name %in% top_artists_monthly, ]
  df_temp1 <- df_temp1[order(df_temp1$hour, decreasing = TRUE), ]
  return(df_temp1)
}) %>% do.call(rbind, .)


df_filtered <- df_condensed
df_filtered <- df_filtered[df_filtered$year == this_year, ]
df_filtered <- df_filtered[order(df_filtered$timecode, decreasing = FALSE), ]
timeCodeToX <- HashMap$new()
devnull <- lapply(seq_down(df_filtered), function(x){
  curr_key <- paste0("KEY_", df_filtered$timecode[x])
  if(timeCodeToX$containsKey(curr_key) == FALSE){
    timeCodeToX$put(curr_key, timeCodeToX$size())
  }
})
max_hours <- lapply(df_filtered$timecode %>% u, function(x){sum(df_filtered$hour[df_filtered$timecode==x])}) %>% unlist %>% max
df_filtered$rowID <- lapply(seq_down(df_filtered), function(x){timeCodeToX$get( paste0("KEY_", df_filtered$timecode[x]))}) %>% unlist + 1
df_filtered$total_a_time <- lapply(df_filtered$master_metadata_album_album_name, function(x){df_filtered$hour[df_filtered$master_metadata_album_album_name==x] %>% sum}) %>% unlist
df_filtered$master_metadata_album_album_name <- reorder(df_filtered$master_metadata_album_album_name, df_filtered$total_a_time, decreasing = FALSE)
df_filtered$master_metadata_album_album_name <- factor(df_filtered$master_metadata_album_album_name, levels=levels(df_filtered$master_metadata_album_album_name))
g21 <- ggplot(df_filtered, aes(fill=master_metadata_album_album_name, y=hour, x = rowID, label = master_metadata_album_album_name)) + 
  geom_bar(position="stack", stat="identity") +
  scale_x_continuous(breaks = df_filtered$rowID %>% u, labels = month.name[df_filtered$month %>% u %>% as.numeric()]) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  xlab("") + 
  ylab("Hours Listened") + 
  ggtitle(paste0("Spotify top ", TOP_N_ARTIST, " albums by month, past year")) + 
  scale_fill_manual(name = "Artist", values = gg_color_hue(df_filtered$master_metadata_album_album_name %>% lu) %>% my_rev) + 
  scale_y_continuous(breaks=seq(0, max_hours, 5)) + 
  theme(legend.position="none")
ggsave(paste0(OUT_DIR, "top_albums_by_month_past_year.pdf"), g21, width = 22, height = 10, units = "in", limitsize = FALSE)
print(g21)
```
  

# top tracks by month?
```{r}
trackToLength <- HashMap$new()
trackToLengths <- HashMap$new()
trackToName <- HashMap$new()

temp1 <- lapply(seq_down(df6), function(x){
  curr_track <- df6$spotify_track_uri[x]
  if(is.null(curr_track)){return(x)}
  
  trackToLengths$append(curr_track, df6$ms_played[x])    
  trackToName$put(curr_track, df6$master_metadata_track_name[x])
  
  return(0)
}) %>% unlist
temp1 <- lapply(trackToLengths$keySet(), function(x){trackToLength$put(x, median(trackToLengths$get(x)))})



TOP_N_ARTIST <- 8
df6$binID <- paste0(df6$timecode, "__", df6$spotify_track_uri )
df_monthly <- lapply(df6$binID %>% u, function(x){
  df_temp <- df6[df6$binID == x, ]
  rval <- data.frame(spotify_track_uri  = df_temp$spotify_track_uri[1],
                     master_metadata_track_name = df_temp$master_metadata_track_name[1],
                     year = df_temp$year[1], 
                     month = df_temp$month[1], 
                     timecode = df_temp$timecode[1],
                     binID = df_temp$binID[1],
                     time_minute = sum(df_temp$ms_played)/60000)
  rval$n_listens <- rval$time_minute / (trackToLength$get(df_temp$spotify_track_uri[1])/60000)
  return(rval)
}) %>% do.call(rbind, .)
df_monthly$hour <- df_monthly$time_minute / 60
df_monthly$label <- paste0(df_monthly$master_metadata_track_name, " (", round(df_monthly$n_listens), ")")

df_condensed <- df_monthly
df_condensed <- lapply(df_monthly$timecode %>% u, function(x){
  df_temp <- df_monthly[df_monthly$timecode == x, ]
  top_tracks_monthly <- df_temp$spotify_track_uri[order(df_temp$hour, decreasing = TRUE)][1:TOP_N_ARTIST]
  df_temp1 <- df_temp[df_temp$spotify_track_uri  %in% top_tracks_monthly, ]
  df_temp1 <- df_temp1[order(df_temp1$hour, decreasing = TRUE), ]
  return(df_temp1)
}) %>% do.call(rbind, .)


df_filtered <- df_condensed
df_filtered <- df_filtered[order(df_filtered$timecode, decreasing = FALSE), ]
timeCodeToX <- HashMap$new()
devnull <- lapply(seq_down(df_filtered), function(x){
  curr_key <- paste0("KEY_", df_filtered$timecode[x])
  if(timeCodeToX$containsKey(curr_key) == FALSE){
    timeCodeToX$put(curr_key, timeCodeToX$size())
  }
})
max_hours <- lapply(df_filtered$timecode %>% u, function(x){sum(df_filtered$hour[df_filtered$timecode==x])}) %>% unlist %>% max
df_filtered$rowID <- lapply(seq_down(df_filtered), function(x){timeCodeToX$get( paste0("KEY_", df_filtered$timecode[x]))}) %>% unlist + 1
df_filtered$total_a_time <- lapply(df_filtered$spotify_track_uri , function(x){df_filtered$hour[df_filtered$spotify_track_uri ==x] %>% sum}) %>% unlist
df_filtered$spotify_track_uri  <- reorder(df_filtered$spotify_track_uri , df_filtered$total_a_time, decreasing = FALSE)
df_filtered$spotify_track_uri  <- factor(df_filtered$spotify_track_uri , levels=levels(df_filtered$spotify_track_uri ))
g22 <- ggplot(df_filtered, aes(fill=spotify_track_uri , y=hour, x = rowID, label = label )) + 
  geom_bar(position="stack", stat="identity") +
  scale_x_continuous(breaks = df_filtered$rowID %>% u, labels = month.name[df_filtered$month %>% u %>% as.numeric()]) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  xlab("") + 
  ylab("Hours Listened") + 
  ggtitle(paste0("Spotify top ", TOP_N_ARTIST, " Songs by month, past year")) + 
  scale_fill_manual(name = "Artist", values = gg_color_hue(df_filtered$spotify_track_uri %>% lu) %>% my_rev) + 
  scale_y_continuous(breaks=seq(0, max_hours+5, 2)) +
  theme(legend.position="none")
ggsave(paste0(OUT_DIR, "top_songs_by_month_past_year.pdf"), g22, width = 14, height = 12, units = "in", limitsize = FALSE)
print(g22)
```
  
usual listening time, by second resolution
```{r}
df00 <- df6
df00$POSIX_TIME <- as.POSIXct(df00$ts, format="%Y-%m-%dT%H:%M:%OSZ", tz="UTC")
df00$PST <- df00$POSIX_TIME %>% format(tz="US/Pacific" ,usetz=TRUE)
df00$timestamp_key <- df00$PST %>% str_extract("(?<=[:space:])[:digit:]{2}:[:digit:]{2}:[:digit:]{2}(?=[:space:])")
df00$second_increment <- floor( df00$ms_played / 1000)
# df00$stop_time <- df00$PST + floor(df00$ms_played/1000)

timestamps <- expand.grid(0:59, 0:59, 0:23)
timestamps$Var1 <- sprintf("%02d", timestamps$Var1)
timestamps$Var2 <- sprintf("%02d", timestamps$Var2)
timestamps$Var3 <- sprintf("%02d", timestamps$Var3)
timestamps$key <- paste0(timestamps$Var3, ":", timestamps$Var2, ":", timestamps$Var1)

timeToCount <- HashMap$new()
for(key in timestamps$key){
  timeToCount$put(key, 0)
}

timestamp_key_to_index <- HashMap$new()
for(i in seq_down(timestamps)){
  timestamp_key_to_index$put(timestamps$key[i], i)
}

timestamp_index_to_key <- HashMap$new()
for(i in seq_down(timestamps)){
  timestamp_index_to_key$put(as.character(i), timestamps$key[i])
}

N_TIMESTAMPS <- nrow(timestamps)
t1 <- Sys.time()
for(i in seq_down(df00)){
  my_key <- df00$timestamp_key[i]
  timeToCount$put(my_key, timeToCount$get(my_key) + 1)
  my_len <- df00$second_increment[i]
  if(my_len > 0){
    for(k in seq(1, my_len)){
      next_key <- timestamp_index_to_key$get(as.character(
        ((timestamp_key_to_index$get(my_key) + k) %% N_TIMESTAMPS) + 1 
      ))
      timeToCount$put(next_key, timeToCount$get(next_key) + 1)
    }
  }
}
print(Sys.time() - t1)

timestamps$count <- lapply(timestamps$key, function(key){
  timeToCount$get(key)
}) %>% unlist
timestamps$x <- seq_down(timestamps)

g23 <- ggplot(timestamps, aes(x=x, y=count)) + 
  geom_jitter(alpha=0.05, color=wes_palette("Darjeeling2")[2], width = 0, height = 0.5) +
  scale_x_continuous(breaks = seq(from=1, to=90000, by=3600), labels = c("12AM", paste0(1:11, "AM"), "12PM", paste0(1:11, "PM"), "12AM")) +
  ggtitle(paste0("Average Daily Listening Activity, past year")) + 
  theme(axis.text.y=element_blank(), 
        axis.ticks.y=element_blank(),
        axis.title.y=element_blank(),
        axis.title.x = element_blank())
plot(g23)


ggsave(paste0(OUT_DIR, "average_listening_activity_past_year.pdf"), g23, width = 16, height = 8, units = "in", limitsize = FALSE)

```
```{r}
df00 <- df6
df00$PST_day_val <- df00$PST %>% as.POSIXct(format="%Y-%m-%d", tz="US/Pacific")
df00$timestamp_key <- df00$PST %>% str_extract("(?<=[:space:])[:digit:]{2}:[:digit:]{2}(?=:[:digit:])")
df00$minute_increment <- floor( df00$ms_played / 60000)

timestamps <- expand.grid(0:59, 0:23)
timestamps$Var1 <- sprintf("%02d", timestamps$Var1)
timestamps$Var2 <- sprintf("%02d", timestamps$Var2)
timestamps$key <- paste0(timestamps$Var2, ":", timestamps$Var1)
timestamps$y_value <- seq_down(timestamps)
timestampToY <- HashMap$new()
timestampToY$populate(timestamps, "key", "y_value")

df_gg <- lapply(seq_down(df00), function(x){
  starting_y_val <- timestampToY$get(df00$timestamp_key[x])
  df_temp <- data.frame(PST_day_val = df00$PST_day_val[x], 
                        y_val = seq(starting_y_val, starting_y_val - df00$minute_increment[x]))
  return(df_temp)
}) %>% do.call(rbind, .)

ggplot(df_gg, aes(x = PST_day_val, y = y_val)) + 
  geom_point(alpha=0.1, color=wes_palette("Darjeeling2")[2]) + 
  scale_y_continuous(breaks = seq(from=1, to=1441, by=60), labels = c("12AM", paste0(1:11, "AM"), "12PM", paste0(1:11, "PM"), "12AM"))

df_g2 <- data.frame(PST_day_val = u(df00$PST_day_val), 
                    count = lapply(u(df00$PST_day_val), function(x){
                      sum(df_gg$PST_day_val==x)
                    }) %>% unlist)
ggplot(df_g2, aes(x = PST_day_val, y = count)) + 
  geom_bar(stat="identity", color=wes_palette("Darjeeling2")[2], fill=wes_palette("Darjeeling2")[2])



```
  
TODO: maybe change this to some sort of sliding window or bin by week?
df5$POSIX_TIME <- as.POSIXct(df5$ts, format="%Y-%m-%dT%H:%M:%OSZ", tz="UTC")
df5$PST <- df5$POSIX_TIME %>% format(tz="US/Pacific" ,usetz=TRUE)

  
  
heatmap
x is month, y is day time
```{r}
N_BINS <- 24

df00 <- df6
df00$POSIX_TIME <- as.POSIXct(df00$ts, format="%Y-%m-%dT%H:%M:%OSZ", tz="UTC")
df00$PST <- df00$POSIX_TIME %>% format(tz="US/Pacific" ,usetz=TRUE)
df00$timestamp_key <- df00$PST %>% str_extract("(?<=[:space:])[:digit:]{2}:[:digit:]{2}(?=:)")
df00$minute_increment <- floor( df00$ms_played / 60000)

timestamps <- expand.grid(0:59, 0:23)
timestamps$Var1 <- sprintf("%02d", timestamps$Var1)
timestamps$Var2 <- sprintf("%02d", timestamps$Var2)
timestamps$key <- paste0(timestamps$Var2, ":", timestamps$Var1)
timestamps$y_time <- seq_down(timestamps)

monthToTimeStamps <- HashMap$new()
for(month in u(timestamps$Var2)){
  monthToTimeStamps$put(month, HashMap$new())
  for(key in timestamps$key){
    monthToTimeStamps$get(month)$put(key, 0)
  }  
}

# get counts per month per timestamp
for(i in seq_down(df00)){
  my_month <- df00$month[i]
  my_key <- df00$timestamp_key[i]
  monthToTimeStamps$get(my_month)$put(my_key, monthToTimeStamps$get(my_month)$get(my_key) + 1)
  my_len <- df00$minute_increment[i]
  if(my_len > 0){
    for(k in seq(1, my_len)){
      next_key <- timestamps$key[((which(timestamps$key==my_key) + k) %% nrow(timestamps)) + 1]
      monthToTimeStamps$get(my_month)$put(next_key, monthToTimeStamps$get(my_month)$get(next_key) + 1)
    }
  }
}

# convert back to DF
df_heat <- expand.grid(0:59, 0:23, seq(1, lu(df00$month)))
df_heat$y_time <- rep(seq(1, max(timestamps$y_time)), lu(df00$month))
df_heat$Var1 <- sprintf("%02d", df_heat$Var1)
df_heat$Var2 <- sprintf("%02d", df_heat$Var2)
df_heat$key <- paste0(df_heat$Var2, ":", df_heat$Var1)
df_heat$month <- sprintf("%02d", df_heat$Var3)

df_heat$count <- lapply(seq_down(df_heat), function(i){
  curr_month <- df_heat$month[i]
  curr_key <- df_heat$key[i]
  monthToTimeStamps$get(curr_month)$get(curr_key)
}) %>% unlist
df_heat$scaled_count <- (df_heat$count-min(df_heat$count))/(max(df_heat$count)-min(df_heat$count))

bin_width <- nrow(timestamps)/N_BINS
df_heat$small_bin <- rep(rep(seq(1, N_BINS), each=bin_width), lu(df_heat$month))
df_heat$small_bin_key <- paste0(df_heat$month, "_", df_heat$small_bin)
df_heat$bin_count <- lapply(seq_down(df_heat), function(i){
  sum(df_heat$count[df_heat$small_bin_key==df_heat$small_bin_key[i]])
}) %>% unlist
df_heat$scaled_count_bin <- (df_heat$bin_count-min(df_heat$bin_count))/(max(df_heat$bin_count)-min(df_heat$bin_count))
df_heat$scaled_count_bin_by_month <- lapply(seq_down(df_heat), function(i){
  curr_month <- df_heat$month[i]
  min_val <- min(df_heat$bin_count[df_heat$month==curr_month])
  max_val <- max(df_heat$bin_count[df_heat$month==curr_month])
  curr_bin_val <- df_heat$bin_count[i]
  rval <- (curr_bin_val-min_val)/(max_val-min_val)
  return(rval)
}) %>% unlist

df_heat$shifted_month <- ((df_heat$Var3 + as.numeric(df6$month[nrow(df6)]) - 1) %% 12) + 1

g25 <- ggplot(df_heat, aes(x=Var3, y=y_time, fill=scaled_count_bin_by_month)) + 
  geom_tile() + 
  scale_y_continuous(breaks = seq(from=1, to=1500, by=60), labels = c("12AM", paste0(1:11, "AM"), "12PM", paste0(1:11, "PM"), "12AM")) + 
  scale_x_continuous(breaks = df_heat$Var3  %>% u, labels = month.name[df_heat$shifted_month %>% u]) +
  theme(axis.title.y=element_blank(), 
        axis.title.x = element_blank(),
        legend.position="none") +
  ggtitle(paste0("Listening Activity Heatmap, past year. scaled by month")) #+ scale_fill_gradient(low = "darkblue", high = "lightskyblue1")

plot(g25)

ggsave(paste0(OUT_DIR, "heatmap_listening_activity_month_past_year.pdf"), g25, width = 11, height = 9, units = "in", limitsize = FALSE)
```


heatmap
x is month, y is day time
```{r}
N_BINS <- 24


weekday_labels <- c("Sunday", "Monday", "Tuesday",  "Wednesday", "Thursday", "Friday", "Saturday")

df00 <- df6
df00$POSIX_TIME <- as.POSIXct(df00$ts, format="%Y-%m-%dT%H:%M:%OSZ", tz="UTC")
df00$PST <- df00$POSIX_TIME %>% format(tz="US/Pacific" ,usetz=TRUE)
df00$timestamp_key <- df00$PST %>% str_extract("(?<=[:space:])[:digit:]{2}:[:digit:]{2}(?=:)")
df00$minute_increment <- floor( df00$ms_played / 60000)

df00$dayoftheweek <-  weekdays(as.Date(df00$PST %>% str_extract("...-..-..")))

timestamps <- expand.grid(0:59, 0:23)
timestamps$hour <- sprintf("%02d", timestamps$Var1)
timestamps$minute <- sprintf("%02d", timestamps$Var2)
timestamps$key <- paste0(timestamps$minute, ":", timestamps$hour)
timestamps$y_time <- seq_down(timestamps)

weekToTimeStamps <- HashMap$new()
for(day in weekday_labels){
  weekToTimeStamps$put(day, HashMap$new())
  for(key in timestamps$key){
    weekToTimeStamps$get(day)$put(key, 0)
  }  
}

# get counts per month per timestamp
for(i in seq_down(df00)){
  my_day <- df00$dayoftheweek[i]
  my_key <- df00$timestamp_key[i]
  weekToTimeStamps$get(my_day)$put(my_key, weekToTimeStamps$get(my_day)$get(my_key) + 1)
  my_len <- df00$minute_increment[i]
  if(my_len > 0){
    for(k in seq(1, my_len)){
      next_key <- timestamps$key[((which(timestamps$key==my_key) + k) %% nrow(timestamps)) + 1]
      weekToTimeStamps$get(my_day)$put(next_key, weekToTimeStamps$get(my_day)$get(next_key) + 1)
    }
  }
}

# convert back to DF
df_heat <- expand.grid(0:59, 0:23, seq(1, lu(df00$dayoftheweek)))
df_heat$y_time <- rep(seq(1, max(timestamps$y_time)), lu(df00$dayoftheweek))
df_heat$Var1 <- sprintf("%02d", df_heat$Var1)
df_heat$Var2 <- sprintf("%02d", df_heat$Var2)
df_heat$key <- paste0(df_heat$Var2, ":", df_heat$Var1)
df_heat$day <- weekday_labels[df_heat$Var3]

df_heat$count <- lapply(seq_down(df_heat), function(i){
  curr_day <- df_heat$day[i]
  curr_key <- df_heat$key[i]
  weekToTimeStamps$get(curr_day)$get(curr_key)
}) %>% unlist
df_heat$scaled_count <- (df_heat$count-min(df_heat$count))/(max(df_heat$count)-min(df_heat$count))

bin_width <- nrow(timestamps)/N_BINS
df_heat$small_bin <- rep(rep(seq(1, N_BINS), each=bin_width), lu(df_heat$day))
df_heat$small_bin_key <- paste0(df_heat$day, "_", df_heat$small_bin)
df_heat$bin_count <- lapply(seq_down(df_heat), function(i){
  sum(df_heat$count[df_heat$small_bin_key==df_heat$small_bin_key[i]])
}) %>% unlist
df_heat$scaled_count_bin <- (df_heat$bin_count-min(df_heat$bin_count))/(max(df_heat$bin_count)-min(df_heat$bin_count))
df_heat$scaled_count_bin_by_day <- lapply(seq_down(df_heat), function(i){
  curr_day <- df_heat$day[i]
  min_val <- min(df_heat$bin_count[df_heat$day==curr_day])
  max_val <- max(df_heat$bin_count[df_heat$day==curr_day])
  curr_bin_val <- df_heat$bin_count[i]
  rval <- (curr_bin_val-min_val)/(max_val-min_val)
  return(rval)
}) %>% unlist

g26 <- ggplot(df_heat, aes(x=Var3, y=y_time, fill=scaled_count_bin)) + 
  geom_tile() + 
  scale_y_continuous(breaks = seq(from=1, to=1500, by=60), labels = c("12AM", paste0(1:11, "AM"), "12PM", paste0(1:11, "PM"), "12AM")) + 
  scale_x_continuous(breaks = df_heat$Var3  %>% u, labels = weekday_labels) +
  theme(axis.title.y=element_blank(), 
        axis.title.x = element_blank(),
        legend.position="none") +
  ggtitle(paste0("Weekly Listening Activity Heatmap, past year.")) 


plot(g26)

ggsave(paste0(OUT_DIR, "heatmap_listening_activity_week_past_year.pdf"), g26, width = 11, height = 9, units = "in", limitsize = FALSE)
```

  
  
```{r}
df6$binID <- paste0(df6$timecode)
df_monthly <- lapply(df6$binID %>% u, function(x){
  df_temp <- df6[df6$binID == x, ]
  rval <- data.frame(n_artists = df_temp$master_metadata_album_artist_name %>% lu,
                     n_songs = df_temp$spotify_track_uri %>% lu,
                     binID = x, 
                     timecode = x, 
                     month = df_temp$month[1] %>% as.numeric)
  return(rval)
}) %>% do.call(rbind, .)
df_monthly <- df_monthly[order(df_monthly$binID, decreasing = FALSE), ]
df_monthly$rowID <- seq_down(df_monthly)

df_filtered <- df_monthly
g27 <- ggplot(df_filtered, aes(fill=n_artists, y=n_artists, x = rowID)) + 
  geom_bar(position="stack", stat="identity") +
  scale_x_continuous(breaks = df_filtered$rowID, labels = month.name[df_filtered$month %>% u %>% as.numeric()]) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  xlab("") + 
  ylab("# unique artists") + 
  ggtitle(paste0("unique artists played, past year")) + 
  theme(legend.position="none") ; g27
ggsave(paste0(OUT_DIR, "unique artists played, past year.pdf"), g27, width = 22, height = 10, units = "in", limitsize = FALSE)

g28 <- ggplot(df_filtered, aes(fill=n_songs, y=n_songs, x = rowID)) + 
  geom_bar(position="stack", stat="identity") +
  scale_x_continuous(breaks = df_filtered$rowID, labels = month.name[df_filtered$month %>% u %>% as.numeric()]) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  xlab("") + 
  ylab("# unique songs") + 
  ggtitle(paste0("unique songs played, past year")) + 
  theme(legend.position="none") ; g28
ggsave(paste0(OUT_DIR, "unique songs played, past year.pdf"), g28, width = 22, height = 10, units = "in", limitsize = FALSE)
```



Things to add
trends?? +/- change in listening time or something??? which
